### 2013-06-12 ms_V3.tex
Initial file upload

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{color,lineno,setspace,graphicx,multirow,kpfonts}
\usepackage[top=2.4cm,left=2.4cm,top=2.4cm,bottom=2.4cm,includefoot]{geometry}
\usepackage[style=bes]{biblatex}
\bibliography{./library, EKLOF,CHEUNG,THUILLER,CANARD, POISOT, WILLIAMS, HAVENS, BAISER, PEREIRA, WHITEHEAD, STOUFFER, STOU2, ALLESINA, ALLOUCHE, ALBOUY, FROESE, JACKSON}
%\bibliograph{library}

\begin{document}

\linenumbers 
\modulolinenumbers[1]

\textbf{Title:}   Inferring food web structure from predator-prey body size relationships\\

\textbf{Authors:}  Dominique Gravel$^{1,2,*}$, Timoth\'ee Poisot$^{1,2}$, Camille Albouy$^{3,4}$, Laure Velez$^{3}$, David Mouillot$^{3,5}$\\

1: Canada Research Chair on Terrestrial Ecosystems. D\'epartement de biologie, chimie et g\'eographique, Universit\'e du Qu\'ebec \`a Rimouski, 300 All\'ee des Ursulines, Qu\'ebec, Canada. G5L 3A1.\\

2: Qu\'ebec Centre for Biodiversity Sciences, Stewart Biological Sciences Building, 1205 Dr.~Penfield Avenue, Montr\'eal (QC), H3A 1B1, Canada

3: UMR CNRS-UM2-IRD-IFREMER 5119 ECOSYM, Universit\'e Montpellier 2, CC 093, 34095 Montpellier Cedex5, France.\\

4: Laboratoire Ecosystèmes Marins Exploit\'es UMR 212, IRD, IFREMER, UMII, UMI, avenue Jean Monnet BP171, 34203 Sete Cedex, France.\\

5: ARC Centre of Excellence for Coral Reef Studies, James Cook University, Townsville, Qld 4811, Australia\\

* Corresponding author. {\tt dominique\_gravel@uqar.ca}. Tel: 1-418-723-1986 \#1752. Fax: 1-418-724-1849.\\

\textbf{Keywords:} Metaweb, Body size, Niche model, Food web\\

\textbf{Words in the abstract:}      179

\textbf{Words in the main text:}     2819

\textbf{Words in the legends:}       423

\textbf{References:}                   45

\textbf{Figures:}                       6

\textbf{Table:}                         0

\newpage
\doublespacing

\section*{Abstract}
Current global changes make it important to be able to predict which
interactions will occur in emerging ecosystems. Most of the current methods to
infer the existence of interactions between two species require a good
knowledge of their behaviour or a direct observation of interactions. In this paper, we
overcome these limitations by developing a method, inspired from the niche
model of food web structure, using the statistical relationship between predator and prey body size to infer the matrix of potential interactions among a pool of species. 
The novelty of our approach is to infer, for any species of a given species pool, the three species specific parameters of the niche model. It allows one to evaluate the feeding interactions of a new species entering the community. We find that this method gives robust predictions of the structure of
food webs, and that its efficiency is increased when the strength of the body-
size relationship between predators and preys increases. We finally illustrate the potential of the method to infer the metaweb structure of pelagic fishes of the Meditarrannean sea under different global change scenarios.
\newpage

%------------------------------------------------------------
\section{Introduction}
One of the current challenges in ecology is to predict the emergence and re-assembly of communities following species responses to global changes. Understanding this is made all the more important as these emergent ecosystems will be more common with increasing human pressure. We know that species invasions, biomass harvesting, ranges shifts, disturbances and changes in land use are important drivers of biodiversity turnover. How they affect species composition is now well described \parencite{Pereira2010}, but forecasting their impact on community structure and functioning requires \emph{a priori} knowledge of potential interactions among species. Predicting interactions among species that never co-occurred proves challenging, as traditional empirical methods of food web sampling such as stomacal content analysis cannot be applied. While for competitive communities this task could be achieved using predictive modeling based on functional traits \parencite{McGill2006, Albouy2010} or phylogeny \parencite{Cavender-Bares2009, Mouquet2012} , it is much more difficult to forecast trophic interactions in a food web \parencite{Ings2009, Tylianakis2008,Montoya2010}.

Inferring potential interactions among species of an arbitrary defined pool is a major step to predict the structure of emergent communities and their functioning. We call these potential interactions among species from a regional pool the \emph{metaweb} \parencite{Dunne2006}. A metaweb takes the form of an adjacency matrix $\mathbf{M}$, of size $s\times s$ for a pool of $s$ species, and in which $\mathbf{M_{ij}} = 1$ if species $i$ can consume species $j$, and $0$ otherwise. This matrix aggregates the trophic interactions among all species from the pool that are susceptible to both co-occur and interact at the regional scale \parencite{Dunne2006}. With a metaweb in hands, one could analyze the impacts of global changes, such as range shifts or species invasions, on the potential community structure, by extracting the relevant species and examining the properties of the community they define. While this concept is progressively finding its way through theoretical spatial food web ecology \parencite{Lafferty2010, Pillai2009, Gravel2011a, Gravel2011b}, it is still limited by data availability and predictive accuracy. Published metaweb data rely on literature surveys \parencite{Havens1992, Piechnik2008, Baiser2012}, or a compilation of several local food webs \parencite{Stanko2002, Poisot2012a}, making them resolved only for species that co-occurred a large enough number of times.

Development of predictive models of trophic interactions could greatly improve our understanding of large scale food web structure and our capacity to anticipate major changes in ecosystem functionning. Theory should provide some guidance about the general rules underpinning interactions among a set of species and thus help us to infer the metaweb. The actual food web theory is largely derived from the niche model \parencite{Williams2000}. This model simply and intuitively poses that each species in a food web has a niche position $n_i$, a feeding niche optimum $c_i$ and a range $r_i$ of suitable preys around that optimum (Fig. 1). These simples rules are sufficient to generate realistic food web structures that fit most of published food webs \parencite{Dunne2006}. The niche model was a substantial improvement of the previous cascade model (Cohen1990) and subsequent models (e.g. the nested hierachy model \parencite{Cattin2004}, the minimum potential model \parencite{Allesina2008}, the probabilistic niche model \parencite{Williams2010} are somehow derived from these rules \parencite{Stouffer2005}. Although it is based on different assumptions, the adaptive foraging theory of food web structure \parencite{Petchey2008b} provides comparable predictions \parencite{Williams2010}. One major recent breakthrough in food web theory have been the attempts to parameterize the niche model and other food web models from field data and to compare their fit through likelihood methods \parencite{Allesina2008, Williams2010, Williams2011}. These methods provide, for each species of the food web, the optimal parameters to fit the empirical web structures, given the hypothesized underlying rules of the niche model.

Despite their theoretical interest, these methods however come with several drawbacks when comes the time to perform biodiversity scenarios. Firstly, they are difficult to apply at large scale because of the technical and logistical requirements of metaweb data collection. Secondly, once the model is parameterized, it could only be used to infer feeding interactions between species with already documented interactions (i.e. it is impossible to infer potential interactions among species that do never co-occurred). Finally, the model optimization is a serious challenge for large datasets with a large number of parameters to evaluate and rough likelihood surfaces. There is consequently an urgent need for a method that could rapidly and easily provide an estimate of potential interactions in a metaweb based on incomplete data.

In this paper, we present a method designed to infer the potential interactions between all pairs of species of a species pool (the metaweb) based on observations of body size of predators and their prey. We do so by a parameterization of the niche model, based on the well-documented allometric scaling relationship between predator and prey \parencite{Cohen2003, Brose2006, Riede2010}. We first develop the method and apply it to food webs from various environments. We find the method accurately predicts the interactions (and lack thereof), and that the accuracy increases with the strength of the predator-prey body size relationship. We then analyze the sensitivity of the method to incomplete data (missing links) and find that it is robust to sampling effort. We finally illustrate the potential of the method to infer the metaweb structure of pelagic fishes of the Meditarrannean sea and the consequences of alteration of body size distribution by global changes or anthropic forcings.

%------------------------------------------------------------
\section{Model description}

The method aims to infer the potential interactions among a pool of species from a subset of observations of predator-prey interactions. The method follows the following steps, with details provided below: 
\begin{itemize}
\item[Step 1:] Log transformation of the body size data;
\item[Step 2:] Statistical analysis of the predator-prey body size relationship;
\item[Step 3:] Inferrence of the niche model parameters for all species from the species pool;
\item[Step 4:] Interpretation of the parameters and computation of the metaweb.
\end{itemize}
We also provide an example of R code (R Core Development Team) and data in the Supplementary Material, detailling the step by step procedure and the format of the input data.

%------------------------------------------------------------
\subsection{Inferring parameters from the niche model and building the metaweb}
The niche model predicts the food web structure from a set of three species-specific parameters: the niche position $n_i$, the feeding niche optimum $c_i$ (called the centroid), and the feeding range $r_i$. A species $i$ will predate all species $j$ whose niche position $n_j$ lies within the interval $[c_i-r_i/2,c_i+r_i/2]$ (Fig. 1). We evaluate all of these parameters from the predator-prey body size relationship, enabling us to parameterize the metaweb from \emph{observed} interactions only. The parameterization is robust to the sampling effort, as it is much easier to document interactions than their absence \parencite{Martinez1999}. Our approach is however mostly limited to predatory interactions since the body size relationship between herbivores and primary producers is not as general \parencite{Riede2010}, and obviously do not hold for parasitic, mutualistic, or competitive networks.

Assuming that body size is the main niche axis structuring trophic interactions, the parameter $n_i$ corresponds simply to the log of body size (in mass or length) of species $i$. Though only the relative position of all species along the body size gradient needs to be respected, it is possible to standardize log body size values between 0 (minimum size in the regional species pool) and 1 (maximal size). We then consider a linear relationship between the decimal logarithm of body size and the centroid of the niche (the dark line at Fig. 1). This relationship is obtained by fitting the linear model $c = \mathrm{log}_{10}(B_{prey})=\alpha_0 + \alpha_1\times\mathrm{log}_{10}(B_{pred})$ to the data, where $B_{prey}$ and $B_{pred}$ are the prey and predator body size respectively. The lower and upper boundaries of the feeding range are easily obtained by fitting the 5\% and 95\% quantile regressions between $\mathrm{log}_{10}(B_{prey})$ and $\mathrm{log}_{10}(B_{pred})$ (the grey lines at Fig. 1, see the example at Fig. 2). We note them as $r_{low,i}$ and $r_{high,j}$ respectively, and the corresponding parameters $\beta_{0,low/high}$ and $\beta_{1,low/high}$.  In sum, the parameter $n_i$ for any species of the metaweb is given by the standardized value of the log body size $B_i$, $c_i$ is estimated from the linear regression between predator and prey log body size and $r_i$ from the quantile regressions.

The next step of the methodology is to reconstruct the metaweb. Once these parameters are calculated from a subsample of species from the regional pool, the coefficients of the different linear models are used to infer the niche parameters of each species of the species pool. Again, the niche parameter for any species $i$, $n_i$, is given by the log of body size. The centroid of the niche is obtained by the relationship $c_i = \alpha_0 + \alpha_1\times\mathrm{n_i}$, the lower boundary of the niche is $r_{low,i} = \beta_{0,low} + \alpha_{1,low}\times\mathrm{n_i}$ and the upper boundary $r_{high,i} = \beta_{0,high} + \alpha_{1,high}\times\mathrm{n_i}$. A feeding link from species $j$ to species $i$ occurs if $n_j > r_{low,i} \& n_j < r_{high,i}$. We provide an example at Fig. 2.

%------------------------------------------------------------
\section{Method accuracy}
\subsection{Predictive performance}
We illustrate the method with the food web datasets of Brose et al. \parencite{Brose2005}. The meta-analysis of Brose \parencite{Brose2006} was conducted on this dataset to test the generality of the predator-prey body size relationship across different systems (terrestrial, aquatic and marine). The relationship was found to be very strong across all systems despite exhibiting variability from one to another. Each web has between 26 and 380 species and 18 and 1466 feeding links. Several of these webs are repetitions over time at a single location, in which cases we pooled the data for each of the 15 different locations to calculate the predator-prey body size relationship. We removed 4 datasets that had a non-significant predator-prey relationship and were thus useless with our approach. The links are not systematically sampled, meaning that any absence of a link between two species for a given dataset could either be a real absence or due to insufficient sampling or lack of information. While the predator-prey body size relationship is very strong over all datasets (Brose2006), there is quite substantial variation among them, enabling us to assess the sensitivity of the method to the strength of this relationship.

We assessed the performance of our method using the True Skill Statistic ($TSS$). The $TSS$ is based on the partition of events (the prediction of a trophic interaction) between four components: the component $a$ reports the number of links that are both predicted and observed, $b$ reports predicted links with no corresponding observation, $c$ reports the number of observed links that are  predicted absent, and $d$ reports the number of predicted and observed absences of links. The TSS is then calculated as $TSS =(ad-bc)/\left[(a+c)(b+d)\right]$. The $TSS$ quantifies the proportion of prediction success relative to false predictions and returns values ranging between 1 (perfect predictions) and -1 (inverted forecast) \parencite{Allouche2006}.

We calculated the $TSS$ for each of the 11 different webs and related it to the strength of the predator-prey body size relationship, measured by the $R^2$ of the linear model. We find that the $TSS$ is positive for all webs, ranging from 0.13 to 0.76 (Fig. 3A). We find a positive relationship between the $R^2$ of the linear model and the $TSS$ ($R^2=0.50$, $p=0.016$). When we decompose the different components of predictions and observations, we find that the fraction of prediction match is high, with an average of $(\overline{a}+\overline{d})/{S^2}=0.58$, Fig. 3B). The fraction of wrong predictions is lower, at $\overline{b+c}/S^2=0.40$, and decreases with the $R^2$ of the predator-prey body size relationship.

The parameterized niche model tends to overestimate the number of links in a web (see the example at Fig. 2). This result is significant but not surprising, given that these datasets do not necessarily contain all links, as they were not designed with this purpose, and thus some of the links might have been missed. This interpretation is also reminiscent of previous debates on the difficulty to sample all links in a web \parencite{Martinez1999}. It is also well known that the niche model predicts a continuous diet along the niche axis (the webs are said to be interval \parencite{Cohen1990, Stouffer2006}), while real food webs do not have this characteristic. We thus might over predict link density within the niche of a given species. Previous studies \parencite{Allesina2008} and the Application 1 however show this problem is easily circumvented when a second niche axis, \emph{e.g.} an environmental niche, comes into play. A recent study on dimensionality of networks shown that most webs have between 3 and 7 dimensions \parencite{Eklof2013}, meaning that adding a few more niche axes can greatly improve the accuracy of predictions.

%------------------------------------------------------------
\subsection{Sensitivity to sampling effort}
We subsequently explored the impact of sampling effort on the accuracy of the model predictions. We assumed a random subsampling of all the interactions occurring in the food web. To do so, we selected a species rich food web ($S = 67$) from the Brose et al. dataset, with 601 observed feeding links and a good $TSS$ (0.51). We randomly removed from 0 to $90\%$ of the observed links to do the evaluation of the parameters of the linear regressions (i.e. e decrease the quantity of information used to calibrate the model). We then after compared the empirical web (with all species) to the inferred web with these parameters (all species also). The comparison was done again with the TSS. We performed 100 randomizations per number of removed links. This numerical simulation reproduces incomplete sampling in the process of building the food web. We find that the $TSS$ remains constant up until $80\%$ of the observed links are removed (Fig. 3). At this level, the $TSS$ starts to decline drastically and its variance increases.

This result shows that our method of parameterization of the niche model is robust with regard to sampling effort. Note however that a biased sampling with respect to body size (e.g. sampling of the largest species) might be more likely to reduce the fit of the predator-prey body size relationship. The aggregation intro trophic species that do have the same body size and the same diet should not impact the prediction since it will not affect parameter evaluation. It will however reduce the fit of the predator-prey body size relationship and therfore the accuracy of the method if the species do have different body sizes. The same artifact will be observed if there is strong intraspecific variation in body size (see the Discussion).

%------------------------------------------------------------
\section{Application: Mediterranean food web structure under fishing pressure}
\subsection{Dataset}
We now present an application of the method to infer the metaweb of interactions among fishes of the Mediterranean sea. The Mediterranean is known as a hotspot of fish diversity that is severely threatened by climate change and overfishing \parencite{Mouillot2011}.There are 557 fish species in the regional pool, with a maximum body size ranging from 2.3 cm to 1100 cm \parencite{Whithead1986, Louisy2005, Froese2011}. Chondrichthyans, mammals and turtles were under represented in the two trophic networks and were removed from the analyses. We parameterized the niche model with a subset of species, from two different highly resolved food webs from the Catalan area \parencite{Coll2006} (82 species) and Corsica \parencite{Albouy2010} (58 species).

\subsection{Inferring the metaweb for Mediterrannean fishes}
We estimated parameters $n$, $c$ and $r$ for each of the 557 species and inferred the potential interactions among all of them (the example in the Supplementariy code is based on this dataset). The metaweb has a total of 126 501 links, for a connectance of 0.41 (Fig. 5A). The metaweb is also highly nested (specialist species feed on a subset of prey of the most generalist species. Fig. 5A). We also considered a second niche axis related to species spatial distribution. Most fish species have restricted geographic range within the Mediterranean sea because of specific response to temperature and other environmental variables \parencite{Albouy2012}. We therefore removed from the metaweb all links between species having no range overlap. Data on the extent of occurrence of fish species were compiled from a published atlas of fishes of the northern Atlantic and the Mediterranean \parencite{Whitehead1986}. This atlas is based on regional data sets and expert knowledge and was edited between 1984 and 1986. It currently provides the only available basin-wide information on the extent of occurrence of all Mediterranean Sea fish species. The above mentioned atlas do not account for the bathymetric distribution of Mediterranean fish species, yet bathymetry is considered as one of the main factors accounting for marine fish distributions \parencite{Louisy2005}. We therefore refined the extent of occurrence maps by clipping off areas with depths that fall outside the minimum or maximum known for the species. Species' bathymetric ranges were obtained from FishBase \parencite{Froese2010, Louisy2005}. The resulting metaweb has a total of 95 989 links, for a connectance of $C = 0.31$. Connectance decreases because links are removed by incomptabilities in bathymetry but the total number of species stays constant. This metaweb is clearly less interval (Fig. 5B). Contiguous gaps in the diet are likely to emerge from modularity in the co-occurrence matrix \parencite{Araujo2011}. Future studies should explore how co-occurrence is constraining the topological structure of metawebs.

%------------------------------------------------------------
\subsection{Impact of global changes}
Our method to parameterize the niche model has a unique feature relative to the original niche model \parencite{Williams2000}: the network properties of the original model, such as the number of links, food chain length and degree distribution (the number of in and out feeding links per species), are controlled by the input parameters (species richness and connectance), wherea all properties of our parameterized niche model are emergent features of the predator-prey body size relationship and the frequency distribution of body size. The connectance in the niche model is fixed by the user; in our case it strongly depends on the scaling of the feeding range with body size and the frequency of larger body species.

This feature is particularly important to understand global change impacts on community structure. For instance, a common prediction of the impact of fisheries on the body size distribution is the reduction in the average and variance of body size \parencite{Jackson2001}. Similarly, global warming is also expected to alter fish body size distribution towards smaller species \parencite{Cheung2012}. We explored by simulations the impact of these changes on the degree distribution of the Mediterranean metaweb. Results are illustrated at Fig. 6. The shape of the cumulative degree distribution provides a visual assessment of the distribution of diet specificity in a network. The curves becomes steeper and the fall moves to the left with increasing specialization (indicative of a larger proportion of species with a low degree). Even if the simulated scenarios are crude representations of the predicted alterations of community structure, they both show that fisheries impacts on body size will substantially alter the network properties. The results at Fig. 6 show that reduction in the average body size will decrease the average number of preys per predator (there is an initial sharper decline of the cumulative distribution), but that super generalist species will also appear (because of the shift of the tail toward the right). The removal of the 40\% largest species reduces much more the average generality which is expect as larger species are predators with a large feeding niche in the niche model. The two scenarios consequently increases substantially the relative abundance of species with a smaller degree, even for the average size reduction scenario where the total number of species is held constant. The change in the degree distribution is likely to reduce substantially the expected persistence and stability of these communities \parencite{Gravel2011a, Gravel2011b}.

%------------------------------------------------------------
\section{Discussion}

In this paper, we presented a method to infer potential interactions among an arbitrary pool of species. The data required to perform this methodology are simple to obtain, as the body size of a large number of species are available from reference databases, or easy to measure. Because we rely on a robust allometric relationship, applying this method requires neither complex statistical techniques, nor an exhaustive knowledge of the realized interactions within the metaweb of interest. In addition to the opportunity to simulate biodiversity scenarios, our method can also help generating baseline expectations about the food web structure for environments which are notoriously difficult to sample, such as soils, deep-sea environments, or fossil records. However, because this allometric relationship is characteristic of predatory interactions, our method will likely not hold for other types of non-body-size structured interactions such as herbivory and parasitism.

Ontogenic shifts in diet are common in many size-structured populations and could be accounted for in two ways with this methodology. First, they will enter the model parameterization by simply including a link from species A (the largest) to species B (the smallest), and the opposite. This would yield in a data point for species B figuring above the 1:1 relationship. Such a data point will obviously influence the model calibration and enlarge the regime of all species. It is not obvious however that ontogenic shifts will be found in the metaweb as it would require an upper limit of the range above the 1:1 relationship. The alternative approach would be to distinguish "sub-species" by size categories in the model calibration and then in the reconstruction of the metaweb. This approach would force ontogenic shifts and perhaps more precisely represent the interaction matrix where the within-population size structure is important.

The method should be completed with other sources of informations to better predict gaps in the interaction matrix. The original niche model was definitely inspired by the predator-prey body size relationship, but was intented to be more general and eventually deal with several niche axes \parencite{Williams2000}. \textcite{Allesina2008} indeed found that adding a second axis, creating gaps into the first axis interaction matrix, increases the fit of the model to empirical data. It also makes the network less interval (a continuous succession of species diets along the niche axis), a structural issue of the niche model that was reported by \textcite{Cattin2004} and \textcite{Bersier2006}. There are numerous sources of information that could be used to improve the model, such as co-occurrence and functional traits.

Our application with the Mediterannean pelagic fish food web provides an example of how straightforward it is to add additional information so as to improve the parameterization. A similar approach could also build on the comptability of other traits such as phenology, location in the water column or hunting modes. While the approach we describe here is based on very simple statistics, the next methodological efforts will also have to take into account more various and heterogeneous sources of data such as phylogeny \parencite{Eklof2012} and expert knowledge. Bayesian inference appears a good candidate to achieve this goal with the possibility to constrain the prior distribution of parameters for each species.

Adding this method to the ecologist's toolbox is a timely issue because there is an urgent need to include interactions into future biodiversity scenarios \parencite{Thuiller2013}. There has been impressive progress in biogeography over the last fifteen years to predict the impact of global changes on range shifts, extinction risks, and the future distribution of biodiversity, but we now face the realization that emerging ecosystems are unlikely to be a spatial displacement of the ones we currently know. This method will help assessing global change impacts of community structure, moving the field of biogeography closer to ecosystem functioning.

\section{Acknowledgements}
We thank I. Gounand for preparing the food web data. DG received financial support from NSERC and Canada Research Chair program. TP is funded by a MELS-FQRNT post-doctoral fellowship.
\newpage

\printbibliography
\newpage

\section*{Figure legends}

\subsection*{Figure 1}
Schematic representation of the niche model and its application to the predator-prey body size relationship. Three consumer species are represented. The white triangles correspond to the niche position of predators (their position on the X axis is transposed along the Y axis). For most cases, prey size is smaller that the predator size and thus fall under the 1:1 relationship. In some occasions, however, the feeding range can overlay the 1:1 relationship, for instance in presence of ontogenic shifts in diet. For a given predator, we consider that the niche centroid ($c_i$) is the average prey size, given by the linear relationship between predator and prey size (black line). The boundaries of the feeding range ($r_i$) are given by the 5\% and 95\% quantile regression lines (dotted lines). A predator feeds on all prey species which their niche lies between these boundaries. In this specific example, the largest predator feeds on the two smaller species (the white triangles depicting the niche lies between range boundaries) and the intermediate size predator feeds on the smallest species.

\subsection*{Figure 2}
Example of predator-prey body size relationship and predictions from the parameterized niche model. Black dots represent observed links while open dots are predicted interactions based on the parameterization of the niche model. The bullseye symbols thus correspond to a match between predicted occurrence of a link and the real data (the "a" classification in the calculation of the TSS, see main text), a black dot a predicted link with not pbservation ("b") and an open circle a non-predicted and observed link ("c"). Data from a creek bed located in Australia \parencite{Brose2005}.

\subsection*{Figure 3}
Performance of the parameterized niche model to predict food web structure for the 11 food webs. A) Relationship between the TSS and the $R^2$ of the predator-prey body size relationship. B) Partitionning of the different components of the TSS.

\subsection*{Figure 4}
Effect of the sampling effort on the accuracy of the parameterized niche model to predict food web structure. The simulation was conducted with the same data as Fig. 2.

\subsection*{Figure 5}
Illustration of the metaweb of the Mediterannean pelagic fishes (interactions in black). Panel A) represents the full metaweb and B) the same metaweb for which links between species not co-occuring together were removed (their range overlap for less than $0.1\%$ of the Mediterannean sea).

\subsection*{Figure 6}
Impacts of altering the body size distribution of Meditarrennean fishes on the degree distribution of the metaweb. The black line corresponds to the original metaweb degree distribution. For the first scenario, we simulated a $40\%$ reduction in average body size and recalculated the metaweb properties, keeping the predator-prey body size relationship constant (dotted line). For the second scenario we eliminated the top $40\%$ largest species and recalculated the metaweb properties (dashed line).

\newpage
\section*{Figures}

\subsection*{Figure 1}

\begin{figure}[ht!]
	\centering\includegraphics[width=0.85\textwidth]{Schema_niche_allometric.pdf}
\end{figure}

\newpage
\subsection*{Figure 2}

\begin{figure}[ht!]
	\centering\includegraphics[width=0.85\textwidth]{Example.pdf}
\end{figure}

\newpage
\subsection*{Figure 3}

\begin{figure}[ht!]
	\centering\includegraphics[width=1\textwidth]{TSS_perweb.pdf}
\end{figure}

\newpage
\subsection*{Figure 4}

\begin{figure}[ht!]
	\centering\includegraphics[width=0.85\textwidth]{TSS_sampling.pdf}
\end{figure}

\newpage
\subsection*{Figure 5}

\begin{figure}[ht!]
	\centering\includegraphics[width=0.6\textwidth]{Example_MED.pdf}
\end{figure}

\newpage
\subsection*{Figure 6}

\begin{figure}[ht!]
	\centering\includegraphics[width=0.85\textwidth]{Degree.pdf}
\end{figure}

\end{document}

### 2013-06-12 replies.tex
Initial file upload

\documentclass [12pt,onecolumn,twoside,openright]{report}
\usepackage[utf8]{inputenc} \usepackage[T1]{fontenc} \usepackage[top=2.4cm,
bottom=2.4cm, left=2.4cm, right=2.4cm]{geometry} \usepackage{setspace}
\usepackage{color}

\begin{document} \begin{onehalfspacing} \begin{center} \large{Response to
Reviewer: Inferring food web structure from predator-prey body size
relationships} \end{center}

Dominique Gravel, Timoth\'ee Poisot, Camille Albouy, Laure Velez, David Mouillot
\begin{center} Reviewer 2: \end{center}

Overall, I think this is an excellent manuscript, nicely written, well explained
(despite some marginal points that might be clarified, see below) and addressing
an important topic. The overall quality of the description of the approach is
above average and addressing these points should be simple.

\medskip \textbf{\large{Main comments:}}

%---------------% 
\medskip \textbf{Comment}: The method assumes a general
relationship between the prey-size range and predator mass. While I think that
this assumption holds when predator and prey are pooled across broad size
classes, I think that many predator groups also have quite specific size ranges.
For instance, we have carried out laboratory studies (Brose et al. 2008, Rall et
al. 2011) with different predator groups on prey that vary in their sizes. Our
general finding were: (1) specific size ranges of prey are attacked, (2) the
lower and upper ends of theses size ranges can be mechanistically explained by
processes that constrain attack rates, and (3) these size ranges (centre and
width) vary across predator groups. The first two points strongly support the
approach presented here by Gravel et al., but the third indicates how
phylogenetic differences between predator groups could cause imprecise
predictions. Although I am a huge fan of this type of allometric scaling work, I
am sure (and I have experienced this quite often) that many other ecologists
would be very interested in an extended discussion where and how phylogenetic
differences among predators could be added to the model.

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

%---------------% 
\medskip \textbf{Comment}: The three regression lines in Fig.
2 demonstrate the mean, maximum and minimum prey size of a predator. I found
this quite intriguing that for a given meta-community, this would predict how
the number of links to resources (the generality of the predator) and the number
of links to consumers (the vulnerability of a resource) depend on the body-mass
on the x-axis of the figure. We have analyzed these relationship for a variety
of food webs (Digel et al. 2011), but I could imagine that the methods
introduced here would allow a more thorough investigation of this relationship.
If possible, a general graph showing the relationship between generality and
predator body mass would be very interesting to see.

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

%---------------% 
\medskip \textbf{Comment}: The decrease of the fraction of
potential links that are realized from local to landscape scales was the central
topic of one of our prior projects (Brose et al. 2004). You might find this
useful to support your assumption that meta-communities should include links
that are not realized at local scales – and meta food webs should thus contain
more links than the sum of the local food webs. This is exactly the pattern that
we documented for different types of ecosystems.

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

%---------------% 
\medskip \textbf{Comment}: My apologies if these points rely
heavily on our own prior work. I found this manuscript very inspiring and also
highly related to our studies. Overall, I would recommend publication of this
manuscript, the minor points listed below should be no obstacle.

%---------------% 
\medskip Line 152: using the abbreviation B (often used for
biomass) for individual mass may be confusing – could be replaced by M.

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

%---------------% 
\medskip Fig. 2: preys should be prey

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

%---------------% 
\medskip Line 214: shouldn't it be up to eight dimensions?

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

%---------------% 
\medskip Some references are incomplete (Eklöf, Mouquet,
Thuiller).

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

%----------------------------------%

\begin{center} Reviewer 3: \end{center}

This paper presents a simple method to infer trophic interactions in food-webs
from information on the body size of the species. While the topic is important
and such a method potentially very useful, I believe that the present work
suffers from many problems.

\medskip \textbf{\large{Main comments:}}

%---------------% 
\medskip \textbf{Comment 1}: It is not clear if the method is
useful to infer a particular food-web (as indicated in the title), or a
"metaweb". I was much confused about the scope of the method, which should be
more clearly stated. From the example with the Mediterranean fishes, it appears
that the proposed approach is useful to build a metaweb. It is not clear to me
if it could be of any use for the description of a "local" food-web. Also, even
at the metaweb level, it is apparent that additional information (spatial
co-occurrence) is needed to obtain a "sensible" metaweb. Ultimately, this
questions the usefulness of the method.

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

%---------------% 
\medskip \textbf{Comment 2}: The authors illustrate the
approach with the use of a food-web based on fishes. It is known that body-size
is important to understand trophic interactions for fishes and for aquatic
systems in general. It is questionable that the approach would be useful for 1)
terrestrial food-webs, and 2) for "complete" food-webs encompassing a larger
array of taxa (this could be circumvented by applying different regressions for
different taxonomic groups; see the paper of Naisbit et al. 2011 in Ecology).

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

%---------------% 
\medskip \textbf{Comment 3}: Important contributions are not
discussed in the manuscript. To my knowledge, the first approach that was able
to predict trophic interactions was given by Ives and Godfray (Am. Nat. 2006),
but based on phylogenetic information (their method is admittedly much more
complex). The authors cite the paper of Petchey et al. (PNAS 2008), but it true
that the aim of their model was surely not to forecast possible interactions.
However, a quite similar approach was proposed by Rohr et al. (Am. Nat. 2010),
which can be easily used to predict interactions. Their first model (Body-size
model) is also very simple, based on the ratio of prey/predator body sizes, and
assumes an optimal ratio (if I am correct, it would be similar to the approach
of the authors with a slope fixed at a value of 1). Because of the simplicity of
the approach, a comparison of both methods could be useful (however, Rohr et al.
approach predicts a total number of interactions that is very close to the
number of interactions used in the "training" food-web; this could be simply
adjusted by decreasing the threshold (see their fig. 1) to a level corresponding
to the 5 and 95\% quantiles used by the authors).

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

%---------------% 
\medskip \textbf{Comment 4}: The authors use Model 1
regression in their analysis. To me, this is problematic as measurement error on
body mass is similar for prey and predators. I recommend the use of Model 2
regression.

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

%---------------% 
\medskip l.50: The use of "emergent" sounds strange here.
Please clarify.

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

%---------------% 
\medskip 2nd paragraph: the metaweb concept is introduced
here, but it is not clear why. If the aim of the authors is to infer a metaweb,
this should be clearly stated here.

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

%---------------% 
\medskip l.128: Here, it is apparent that the authors aim is
to infer a metaweb. Again, this should be clearly stated earlier (and even in
the title?)

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

%---------------% 
\medskip l.139-140: How can you state this here without
performing an analysis? This is unclear to me (at least, this is not intuitive).

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

%---------------% 
\medskip l.155: grey or dotted lines?

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

%---------------% 
\medskip l.157: what are these betas?

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

%---------------% 
\medskip l.167: should the $\alpha_1$ rather be a $\beta_1$
(see my former comment)? Please clarify.

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

%---------------% 
\medskip l.199-201: if I understand correctly Fig. 3, the
increase in TSS is due mostly to the correct prediction of the fraction d
(predicted absences), and not to correctly predicted presences (fraction a),
which is likely the most interesting fraction for any practical reason. This
should be stated.

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

%---------------% 
\medskip l.304: expected, not expect

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

%---------------% 
\medskip l.511: I would not discuss the problem of ontogenic
shift in the figure legend.

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

%---------------% 
\medskip l.515: Is their any justification behind the use of 5
and 95\% quantiles? Why not the usual 2.5 and 97.5\%, or 0 and 100\%?

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

%---------------% 
\medskip l.522: black and open dots: I guess it is the
contrary.

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

%---------------% 
\medskip l. 526: "with not pbservation" ?

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

%---------------% 
\medskip Figure 2: An important difference between the
original and the parameterized niche model is apparent in this figure: here, the
$c_i$ and $r_i$ are constrained by the allometric regression, which is not the
case in the original model. From the distribution of the open dots, this appears
quite problematic in this figure (many open dots are outside the predicted
range; many predicted interactions are not existing), and this questions the
usefulness of the whole approach. Other traits may be needed; perhaps performing
several regressions for different broad taxonomic groups may also improve the
approach, and widen its applicability.

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

\end{onehalfspacing}

\end{document}

### 2013-06-12 code_Figure5.R

@@ -1,0 +1,190 @@
+##############################################
+##############################################
+#
+# R Code supplementing the paper 
+# Inferring food web structure form predator-prey body size relationship
+# by Gravel, Poisot, Albouy, Velez, Mouillot
+# Methods in Ecology and Evolution
+# PUTS THE VOLUME/ISSUE/PAGES HERE
+# February 2013
+# 
+##############################################
+##############################################
+#
+
+#### READ ME #################################
+#
+# The code has the following structure
+# 1. Loading of an artificial dataset of i) predator-prey interactions, ii) body size distribution, iii) hypothetical species presence/absence lists
+# 2. Definition of functions run for the analysis
+# 3. Calculation of the observed parameters for the niche model
+# 4. Inferrence of the parameters for all species in the metaweb
+#
+# Name of the parameters of the niche model
+# n: niche position along the niche axis
+# c: centroid of the niche
+# r: range of the niche
+#
+##############################################
+
+
+##############################################
+# 1.  The mediterranean Application ####### 
+
+# data_loading: please load the R data file
+# This file is a R list object with 4 objects
+# Diet_matrix : predator prey claibration matrix that is a compilation of two resolved food webs, the Catalan Sea and Corsica.
+# BodySize_cal : a vector of species log body size represented in the previous matrix for the model calibration
+# Body_Size_med : log Body size of 557 Mediterranean fish species 
+# Mat_Cooc : Co-ocurence martix 
+
+### Data loading
+load("data.rdata")
+
+
+##############################################
+# 2. Useful functions
+
+
+##############################################
+# Get regression parameters
+# Input arguments:
+# Bprey = log10 biomass of the prey
+# Bpred = log10 biomass of the predator
+# Quartil = a vector of the inferior and the superio quartile c(0.03,0.97)
+# Returns a list of regression objectis
+# Requires the quantreg package
+
+reg_fn = function(Bprey,Bpred,quartil) {
+
+	library(quantreg)
[…]

### 2013-06-12 script_analysis.R

@@ -1,0 +1,355 @@
+##############################################
+# Open the data
+##############################################
+#setwd("/Users/DGravel/Documents/Projects_On_Going/Niche_allometrique/analyse_I")
+setwd("/Users/DGravel/Documents/Manuscripts/2012/Niche_MEE_Sept2012/analysis_II")
+source("get_pars_Niche.R")
+
+data = read.table("pp.txt")[,c(9,20,18,28,2,11,22)]
+data[,5] = as.numeric(data[,5])
+data[,1] = as.character(data[,1])
+data[,2] = as.character(data[,2])
+data[,6] = as.character(data[,6])
+data[,7] = as.character(data[,7])
+
+un_named_1 = data[,1]=="-999"
+data[un_named_1,1] = data[un_named_1,6]
+un_named_2 = data[,2]=="-999"
+data[un_named_2,2] = data[un_named_2,7]
+
+##############################################
+# Figure 1: example
+##############################################
+i = 2
+subdata = subset(data,data[,5]==i)
+nprey = as.character(subdata[,1])
+npred = as.character(subdata[,2])	
+Bpred = log(subdata[,3],10)
+Bprey = log(subdata[,4],10)
+
+B_all = c(Bprey,Bpred)
+dup = duplicated(B_all)
+B = subset(B_all,dup==FALSE)
+sp_all = c(nprey,npred)
+sp = subset(sp_all,dup==FALSE)
+
+library(quantreg)
+mean_reg = lm(Bprey~Bpred)
+qr95 = rq(Bprey~Bpred,tau = .95)
+qr05 = rq(Bprey~Bpred,tau = .05)
+
+quartz(height = 4.5, width = 3.5*1.5)
+par(mar=c(5,4.5,2,1))
+plot(Bpred,Bprey,xlab = "Log10 Body size of predators", ylab = "Log10 Body size of preys",xlim=range(Bpred),cex.lab =1.25, cex.axis=1.)
+abline(mean_reg)
+abline(qr95, col = "grey")
+abline(qr05, col = "grey")
+
+delta = mean_reg$coef[2]
+b1 = mean_reg$coef[1]
+b2 = delta	
+n = B
+c = b1 + b2*B
[…]

### 2013-06-12 ms_V3.tex

@@
 6 show that reduction in the average body size will decrease the average number of preys per predator (there is an initial sharper decline of the cumulative distribution), but that super generalist species will also appear (because of the shift of the tail toward the right).
-The removal of the 40\% largest species reduces much more the average generality which is expect as larger species are predators with a large feeding niche in the niche model.
+The removal of the 40\% largest species reduces much more the average generality which is expected as larger species are predators with a large feeding niche in the niche model.
 The two scenarios consequently increases substantially the relative abundance of species with a smaller degree, even for the average size reduction scenario where the total number of species is held constant.
@@
 Black dots represent observed links while open dots are predicted interactions based on the parameterization of the niche model.
-The bullseye symbols thus correspond to a match between predicted occurrence of a link and the real data (the "a" classification in the calculation of the TSS, see main text), a black dot a predicted link with not pbservation ("b") and an open circle a non-predicted and observed link ("c").
+The bullseye symbols thus correspond to a match between predicted occurrence of a link and the real data (the "a" classification in the calculation of the TSS, see main text), a black dot a predicted link with not observation ("b") and an open circle a non-predicted and observed link ("c").
 Data from a creek bed located in Australia \parencite{Brose2005}.

### 2013-06-13 replies.tex
just two minor corrections
Ref 3, replies 1 and 2

@@
 
-\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}
+\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{As stated
+in the abstract, our method allows to ``infer the matrix of potential
+interactions among a pool of species'', and does so regardless of whether one is
+working at the local or regional scale. In the text, we give examples at both
+these scales (locally in figures 2 and 3, regionnaly in figure 5). We do agree
+with the fact that additional information will make the predictions better; this
+is described at length in the text, and an example of this (including
+co-occurence along the depth gradient) is pictured in Fig. 5b. This is also
+explicitely written in the discussion (L. XXX-XXX).}}
 
@@
 
-\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}
+\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We agree
+that the fit of the model is only as strong as the relationship between prey and
+predator body-size. This is the purpose of Fig. 3; this relationship is also
+described in section 3.1 ``Predictive performance''.}}
 
@@
 
-\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}
+\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We corrected accordingly}}
 

### 2013-06-13 ms_V3.tex

@@
 \section*{Abstract}
+
 Current global changes make it important to be able to predict which
 interactions will occur in emerging ecosystems. Most of the current methods to
-infer the existence of interactions between two species require a good
-knowledge of their behaviour or a direct observation of interactions. In this paper, we
-overcome these limitations by developing a method, inspired from the niche
-model of food web structure, using the statistical relationship between predator and prey body size to infer the matrix of potential interactions among a pool of species. 
-The novelty of our approach is to infer, for any species of a given species pool, the three species specific parameters of the niche model.
-It allows one to evaluate the feeding interactions of a new species entering the community.
-We find that this method gives robust predictions of the structure of
+infer the existence of interactions between two species require a good knowledge
+of their behaviour or a direct observation of interactions. In this paper, we
+overcome these limitations by developing a method, inspired from the niche model
+of food web structure, using the statistical relationship between predator and
+prey body size to infer the matrix of potential interactions among a pool of
+species.  The novelty of our approach is to infer, for any species of a given
+species pool, the three species specific parameters of the niche model. It
+allows one to evaluate the feeding interactions of a new species entering the
+community. We find that this method gives robust predictions of the structure of
 food webs, and that its efficiency is increased when the strength of the body-
-size relationship between predators and preys increases.
-We finally illustrate the potential of the method to infer the metaweb structure of pelagic fishes of the Meditarrannean sea under different global change scenarios.
+size relationship between predators and preys increases. We finally illustrate
+the potential of the method to infer the metaweb structure of pelagic fishes of
+the Meditarrannean sea under different global change scenarios.
+
 \newpage
@@
 \subsection{Inferring parameters from the niche model and building the metaweb}
-The niche model predicts the food web structure from a set of three species-specific parameters: the niche position $n_i$, the feeding niche optimum $c_i$ (called the centroid), and the feeding range $r_i$.
-A species $i$ will predate all species $j$ whose niche position $n_j$ lies within the interval $[c_i-r_i/2,c_i+r_i/2]$ (Fig.
-1).
-We evaluate all of these parameters from the predator-prey body size relationship, enabling us to parameterize the metaweb from \emph{observed} interactions only.
-The parameterization is robust to the sampling effort, as it is much easier to document interactions than their absence \parencite{Martinez1999}.
-Our approach is however mostly limited to predatory interactions since the body size relationship between herbivores and primary producers is not as general \parencite{Riede2010}, and obviously do not hold for parasitic, mutualistic, or competitive networks.
 
-Assuming that body size is the main niche axis structuring trophic interactions, the parameter $n_i$ corresponds simply to the log of body size (in mass or length) of species $i$.
-Though only the relative position of all species along the body size gradient needs to be respected, it is possible to standardize log body size values between 0 (minimum size in the regional species pool) and 1 (maximal size).
-We then consider a linear relationship between the decimal logarithm of body size and the centroid of the niche (the dark line at Fig.
-1).
-This relationship is obtained by fitting the linear model $c = \mathrm{log}_{10}(B_{prey})=\alpha_0 + \alpha_1\times\mathrm{log}_{10}(B_{pred})$ to the data, where $B_{prey}$ and $B_{pred}$ are the prey and predator body size respectively.
-The lower and upper boundaries of the feeding range are easily obtained by fitting the 5\% and 95\% quantile regressions between $\mathrm{log}_{10}(B_{prey})$ and $\mathrm{log}_{10}(B_{pred})$ (the grey lines at Fig.
-1, see the example at Fig.
-2).
-We note them as $r_{low,i}$ and $r_{high,j}$ respectively, and the corresponding parameters $\beta_{0,low/high}$ and $\beta_{1,low/high}$.
-In sum, the parameter $n_i$ for any species of the metaweb is given by the standardized value of the log body size $B_i$, $c_i$ is estimated from the linear regression between predator and prey log body size and $r_i$ from the quantile regressions.
+The niche model predicts the food web structure from a set of three
+species-specific parameters \parencite{Williams2000}: the niche position $n_i$, the feeding niche optimum
+$c_i$ (called the centroid), and the feeding range $r_i$. A species $i$ will
+predate all species $j$ whose niche position $n_j$ lies within the interval
+$[c_i-r_i/2,c_i+r_i/2]$ (Fig. 1). We evaluate all of these parameters from the
+predator-prey body size relationship, enabling us to parameterize the metaweb
+from \emph{observed} interactions only. The parameterization is robust to the
+sampling effort, as it is much easier to document interactions than their
+absence \parencite{Martinez1999}. Our approach is however mostly limited to
+predatory interactions since the body size relationship between herbivores and
+primary producers is not as general \parencite{Riede2010}, and obviously do not
+hold for parasitic, mutualistic, or competitive networks.
+
+Assuming that body size is the main niche axis structuring trophic interactions,
+the parameter $n_i$ corresponds simply to the log of body size (in mass or
+length) of species $i$. Though only the relative position of all species along
+the body size gradient needs to be respected, it is possible to standardize log
+body size values between 0 (minimum size in the regional species pool) and 1
+(maximal size). We then consider a linear relationship between the decimal
+logarithm of body size and the centroid of the niche (the dark line at Fig. 1).
+This relationship is obtained by fitting the linear model $c =
+\mathrm{log}_{10}(B_{prey})=\alpha_0 +
+\alpha_1\times\mathrm{log}_{10}(B_{pred})$ to the data, where $B_{prey}$ and
+$B_{pred}$ are the prey and predator body size respectively. The lower and upper
+boundaries of the feeding range are easily obtained by fitting the 5\% and 95\%
+quantile regressions between $\mathrm{log}_{10}(B_{prey})$ and
+$\mathrm{log}_{10}(B_{pred})$ (the dotted lines at Fig. 1, see the example at Fig.
+2). We note them as $r_{low,i}$ and $r_{high,j}$ respectively, and the
+corresponding parameters $\beta_{0,low/high}$ and $\beta_{1,low/high}$.  In sum,
+the parameter $n_i$ for any species of the metaweb is given by the standardized
+value of the log body size $B_i$, $c_i$ is estimated from the linear regression
+between predator and prey log body size and $r_i$ from the quantile regressions.
 

### 2013-06-14 replies.tex

@@
 
-\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}
+\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{This is a basic
+postulate of the niche model. We have added a reference to the original paper to
+eliminate ambiguity.}}
 
@@
 
-\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}
+\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The
+  \emph{dotted} lines. We corrected accordingly and apologize for the mistake.}}
 
@@
 
-\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}
+\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{No. The centroid
+is a function of the two body sizes (hence $\alpha$), while the range limits are
+a function of the predator body size and its range.}}
 
@@
 
-\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}
+\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{Whether the
+correct prediction of absence or presence of an interaction is the most
+interesting part of a model is ultimately a matter of personal taste, and
+adequation to the study objectives. Given that (especialyl when no other traits
+than body size are included), this method tends to over-estimate the number of
+links, we argue that correctly predicting absences of links is an extremely
+important feature.}}
 
@@
 
-\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We corrected accordingly}}
+\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We corrected
+accordingly.}}
 
@@
 
-\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}
+\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We argue it is an
+important piece of information, which was required by a previous reviewer. We
+made no changes.}}
 
@@
 
-\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}
+\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The fact that our
+model over-predict the number of interactions is abundantly discussed in the
+manuscript (along with why, and how to overcome it), so we will not elaborate
+further on it in this reply. In the original niche model paper, it is true
+that $c$ is not constrained by $n$. However, the purposes of the two models are
+not the same. The niche model allows to generate a distribution of network
+properties based only on connectance and richness. We add allometric
+informations so as to be able to estimate species-level interactions in addition
+to network properties. The allometric relationshipss on which we rely are well
+documented. As for the fact that other traits can be added, this is discussed in
+the manuscript at several places, including a whole figure. We made no changes
+to the manuscript.}}
 

### 2013-06-15 replies.tex
Biblio+figure2+text corrections

@@
 
-\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}
+\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We corrected
+accordingly by replacing the abbrevation B by M}}
 
@@
 
-\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}
+\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We corrected
+accordingly}}
 
@@
 
-\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}
+\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The study of Rohr et al.
+(2010), does not allow to evaluate the parameters of a new species entering the community, neither the metaweb (which is the object of the current study).
+It is therefore not possible to infer the potential links an immigrating species will do with the resident species.
+These methods also require a complete knowledge of the interactions in the community.
+Our method is consequently much more robust than previous methods to infer the parameters of the niche model.
+Based on these arguments, we believe that the method  will be used for instance to study the interactions in emerging communities following global changes.}}
 
@@
 
-\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}
+\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{ We replaced the word "emergent" by "novel".}}
 
@@
 
-\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}
+\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The choice of quantiles are left free to the user in the R code providing with this article, by default, we chose the most commonly used threshold of 5\% and 95\%.
+}}
 
@@
 
-\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}
+\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We corrected accordingly and apologize for the mistake}}
 

### 2013-06-15 ms_V3.tex

@@
 \usepackage[style=bes]{biblatex}
-\bibliography{./library, EKLOF,CHEUNG,THUILLER,CANARD, POISOT, WILLIAMS, HAVENS, BAISER, PEREIRA, WHITEHEAD, STOUFFER, STOU2, ALLESINA, ALLOUCHE, ALBOUY, FROESE, JACKSON}
+\bibliography{./library, EKLOF,CHEUNG,THUILLER,CANARD, POISOT, WILLIAMS, HAVENS, BAISER, PEREIRA, WHITEHEAD, STOUFFER, STOU2, ALLESINA, ALLOUCHE, ALBOUY, FROESE, JACKSON,STANKO}
 %\bibliograph{library}
@@
 One of the current challenges in ecology is to predict the emergence and re-assembly of communities following species responses to global changes.
-Understanding this is made all the more important as these emergent ecosystems will be more common with increasing human pressure.
+Understanding this is made all the more important as these novel ecosystems will be more common with increasing human pressure.
 We know that species invasions, biomass harvesting, ranges shifts, disturbances and changes in land use are important drivers of biodiversity turnover.
@@
 We call these potential interactions among species from a regional pool the \emph{metaweb} \parencite{Dunne2006}.
-A metaweb takes the form of an adjacency matrix $\mathbf{M}$, of size $s\times s$ for a pool of $s$ species, and in which $\mathbf{M_{ij}} = 1$ if species $i$ can consume species $j$, and $0$ otherwise.
+A metaweb takes the form of an adjacency matrix $\mathbf{MW}$, of size $s\times s$ for a pool of $s$ species, and in which $\mathbf{MW_{ij}} = 1$ if species $i$ can consume species $j$, and $0$ otherwise.
 This matrix aggregates the trophic interactions among all species from the pool that are susceptible to both co-occur and interact at the regional scale \parencite{Dunne2006}.
@@
 The method follows the following steps, with details provided below:
-\begin{itemize}
+\begin{description}
 \item[Step 1:] Log transformation of the body size data;
@@
 \item[Step 4:] Interpretation of the parameters and computation of the metaweb.
-\end{itemize}
+\end{description}
 We also provide an example of R code (R Core Development Team) and data in the Supplementary Material, detailling the step by step procedure and the format of the input data.
@@
 This relationship is obtained by fitting the linear model $c =
-\mathrm{log}_{10}(B_{prey})=\alpha_0 +
-\alpha_1\times\mathrm{log}_{10}(B_{pred})$ to the data, where $B_{prey}$ and
-$B_{pred}$ are the prey and predator body size respectively. The lower and upper
+\mathrm{log}_{10}(M_{prey})=\alpha_0 +
+\alpha_1\times\mathrm{log}_{10}(M_{pred})$ to the data, where $M_{prey}$ and
+$M_{pred}$ are the prey and predator body size respectively. The lower and upper
 boundaries of the feeding range are easily obtained by fitting the 5\% and 95\%
-quantile regressions between $\mathrm{log}_{10}(B_{prey})$ and
-$\mathrm{log}_{10}(B_{pred})$ (the dotted lines at Fig. 1, see the example at Fig.
+quantile regressions between $\mathrm{log}_{10}(M_{prey})$ and
+$\mathrm{log}_{10}(M_{pred})$ (the dotted lines at Fig. 1, see the example at Fig.
 2). We note them as $r_{low,i}$ and $r_{high,j}$ respectively, and the
@@
 the parameter $n_i$ for any species of the metaweb is given by the standardized
-value of the log body size $B_i$, $c_i$ is estimated from the linear regression
+value of the log body size $M_i$, $c_i$ is estimated from the linear regression
 between predator and prey log body size and $r_i$ from the quantile regressions.
@@
 Example of predator-prey body size relationship and predictions from the parameterized niche model.
-Black dots represent observed links while open dots are predicted interactions based on the parameterization of the niche model.
+Open dots represent observed links while black dots are predicted interactions based on the parameterization of the niche model.
 The bullseye symbols thus correspond to a match between predicted occurrence of a link and the real data (the "a" classification in the calculation of the TSS, see main text), a black dot a predicted link with not observation ("b") and an open circle a non-predicted and observed link ("c").

### 2013-06-18 SupplementaryCode.R
Dom: final edits

@@ -1,0 +1,189 @@
+##############################################
+##############################################
+#
+# R Code supplementing the paper 
+# Inferring food web structure form predator-prey body size relationship
+# by Gravel, Poisot, Albouy, Velez, Mouillot
+# Methods in Ecology and Evolution
+# PUTS THE VOLUME/ISSUE/PAGES HERE
+# February 2013
+# 
+##############################################
+##############################################
+#
+
+#### READ ME #################################
+#
+# The code has the following structure
+# 1. Loading of an artificial dataset of i) predator-prey interactions, ii) body size distribution, iii) hypothetical species presence/absence lists
+# 2. Definition of functions run for the analysis
+# 3. Calculation of the observed parameters for the niche model
+# 4. Inferrence of the parameters for all species in the metaweb
+#
+# Name of the parameters of the niche model
+# n: niche position along the niche axis
+# c: centroid of the niche
+# r: range of the niche
+#
+##############################################
+
+
+##############################################
+# 1.  The mediterranean Application ####### 
+
+
+### data_loading please load the R data file
+# This file is a R list object with 4 objects
+#Diet_matrix : predator prey claibration matrix that is a compilation of two resolved food webs, the Catalan Sea and Corsica.
+# BodySize_cal : a vector of species log body size represented in the previous matrix for the model calibration
+# Body_Size_med : log Body size of 557 Mediterranean fish species 
+# Mat_Cooc : Co-ocurence martix 
+
+### Data loading
+load("data.rdata")
+
+
+##############################################
+# 2. Useful functions
+
+
+##############################################
+# Get regression parameters
+# Input arguments:
+# Bprey = log10 biomass of the prey
+# Bpred = log10 biomass of the predator
+# Quartil = a vector of the inferior and the superio quartile c(0.03,0.97)
+# Returns a list of regression objectis
+# Requires the quantreg package
+
[…]

### 2013-06-18 ms_V3.tex

@@
 species. The novelty of our approach is to infer, for any species of a given
-species pool, the three species specific parameters of the niche model. It
-allows one to evaluate the feeding interactions of a new species entering the
-community. We find that this method gives robust predictions of the structure of
-food webs, and that its efficiency is increased when the strength of the body-
-size relationship between predators and preys increases. We finally illustrate
-the potential of the method to infer the metaweb structure of pelagic fishes of
-the Meditarrannean sea under different global change scenarios.
+species pool, the three species specific parameters of the niche model. The
+method applies to both local and metaweb scales. It allows one to evaluate the
+feeding interactions of a new species entering the community. We find that this
+method gives robust predictions of the structure of food webs, and that its
+efficiency is increased when the strength of the body- size relationship between
+predators and preys increases. We finally illustrate the potential of the method
+to infer the metaweb structure of pelagic fishes of the Meditarrannean sea under
+different global change scenarios.
 
@@
 \section{Introduction}
-One of the current challenges in ecology is to predict the emergence and re-assembly of communities following species responses to global changes.
-Understanding this is made all the more important as these novel ecosystems will be more common with increasing human pressure.
-We know that species invasions, biomass harvesting, ranges shifts, disturbances and changes in land use are important drivers of biodiversity turnover.
-How they affect species composition is now well described \parencite{Pereira2010}, but forecasting their impact on community structure and functioning requires \emph{a priori} knowledge of potential interactions among species.
-Predicting interactions among species that never co-occurred proves challenging, as traditional empirical methods of food web sampling such as stomacal content analysis cannot be applied.
-While for competitive communities this task could be achieved using predictive modeling based on functional traits \parencite{McGill2006, Albouy2010} or phylogeny \parencite{Cavender-Bares2009, Mouquet2012} , it is much more difficult to forecast trophic interactions in a food web \parencite{Ings2009, Tylianakis2008,Montoya2010}.
+One of the current challenges in ecology is to predict the emergence and
+re-assembly of communities following species responses to global changes.
+Understanding this is made all the more important as these novel ecosystems will
+be more common with increasing human pressure. We know that species invasions,
+biomass harvesting, ranges shifts, disturbances and changes in land use are
+important drivers of biodiversity turnover. How they affect species composition
+is now well described \parencite{Pereira2010}, but forecasting their impact on
+community structure and functioning requires \emph{a priori} knowledge of
+potential interactions among species. Predicting interactions among species that
+never co-occurred proves challenging, as traditional empirical methods of food
+web sampling such as stomacal content analysis cannot be applied. While for
+competitive communities this task could be achieved using predictive modeling
+based on functional traits \parencite{McGill2006, Albouy2010} or phylogeny
+\parencite{Cavender-Bares2009, Mouquet2012} , it is much more difficult to
+forecast trophic interactions in a food web \parencite{Ings2009,
+Tylianakis2008,Montoya2010}.
 
-Inferring potential interactions among species of an arbitrary defined pool is a major step to predict the structure of emergent communities and their functioning.
-We call these potential interactions among species from a regional pool the \emph{metaweb} \parencite{Dunne2006}.
-A metaweb takes the form of an adjacency matrix $\mathbf{MW}$, of size $s\times s$ for a pool of $s$ species, and in which $\mathbf{MW_{ij}} = 1$ if species $i$ can consume species $j$, and $0$ otherwise.
-This matrix aggregates the trophic interactions among all species from the pool that are susceptible to both co-occur and interact at the regional scale \parencite{Dunne2006}.
-With a metaweb in hands, one could analyze the impacts of global changes, such as range shifts or species invasions, on the potential community structure, by extracting the relevant species and examining the properties of the community they define.
-While this concept is progressively finding its way through theoretical spatial food web ecology \parencite{Lafferty2010, Pillai2009, Gravel2011a, Gravel2011b}, it is still limited by data availability and predictive accuracy.
-Published metaweb data rely on literature surveys \parencite{Havens1992, Piechnik2008, Baiser2012}, or a compilation of several local food webs \parencite{Stanko2002, Poisot2012a}, making them resolved only for species that co-occurred a large enough number of times.
+Inferring potential interactions among species of an arbitrary defined pool is a
+major step to predict the structure of emergent communities and their
+functioning. We call these potential interactions among a given set of species, wether
+at the local or regional scales, the \emph{metaweb} \parencite{Dunne2006}. A
+metaweb takes the form of an adjacency matrix $\mathbf{MW}$, of size $s\times s$
+for a pool of $s$ species, and in which $\mathbf{MW_{ij}} = 1$ if species $i$
+can consume species $j$, and $0$ otherwise. This matrix aggregates the trophic
+interactions among all species from the pool that are susceptible to both
+co-occur and interact at the regional scale \parencite{Dunne2006}. With a
+metaweb in hands, one could analyze the impacts of global changes, such as range
+shifts or species invasions, on the potential community structure, by extracting
+the relevant species and examining the properties of the community they define.
+While this concept is progressively finding its way through theoretical spatial
+food web ecology \parencite{Lafferty2010, Pillai2009, Gravel2011a, Gravel2011b},
+it is still limited by data availability and predictive accuracy. Published
+metaweb data rely on literature surveys \parencite{Havens1992, Piechnik2008,
+Baiser2012}, or a compilation of several local food webs \parencite{Stanko2002,
+Poisot2012a}, making them resolved only for species that co-occurred a large
+enough number of times.
 
-Development of predictive models of trophic interactions could greatly improve our understanding of large scale food web structure and our capacity to anticipate major changes in ecosystem functionning.
-Theory should provide some guidance about the general rules underpinning interactions among a set of species and thus help us to infer the metaweb.
-The actual food web theory is largely derived from the niche model \parencite{Williams2000}.
-This model simply and intuitively poses that each species in a food web has a niche position $n_i$, a feeding niche optimum $c_i$ and a range $r_i$ of suitable preys around that optimum (Fig.
-1).
-These simples rules are sufficient to generate realistic food web structures that fit most of published food webs \parencite{Dunne2006}.
-The niche model was a substantial improvement of the previous cascade model (Cohen1990) and subsequent models (e.g.
-the nested hierachy model \parencite{Cattin2004}, the minimum potential model \parencite{Allesina2008}, the probabilistic niche model \parencite{Williams2010} are somehow derived from these rules \parencite{Stouffer2005}.
-Although it is based on different assumptions, the adaptive foraging theory of food web structure \parencite{Petchey2008b} provides comparable predictions \parencite{Williams2010}.
-One major recent breakthrough in food web theory have been the attempts to parameterize the niche model and other food web models from field data and to compare their fit through likelihood methods \parencite{Allesina2008, Williams2010, Williams2011}.
-These methods provide, for each species of the food web, the optimal parameters to fit the empirical web structures, given the hypothesized underlying rules of the niche model.
+Development of predictive models of trophic interactions could greatly improve
+our understanding of large scale food web structure and our capacity to
+anticipate major changes in ecosystem functionning. Theory should provide some
+guidance about the general rules underpinning interactions among a set of
+species and thus help us to infer the metaweb. The actual food web theory is
+largely derived from the niche model \parencite{Williams2000}. This model simply
+and intuitively poses that each species in a food web has a niche position
+$n_i$, a feeding niche optimum $c_i$ and a range $r_i$ of suitable preys around
+that optimum (Fig. 1). These simples rules are sufficient to generate realistic
+food web structures that fit most of published food webs \parencite{Dunne2006}.
+The niche model was a substantial improvement of the previous cascade model
+(Cohen1990) and subsequent models (e.g. the nested hierachy model
+\parencite{Cattin2004}, the minimum potential model \parencite{Allesina2008},
+the probabilistic niche model \parencite{Williams2010} are somehow derived from
+these rules \parencite{Stouffer2005}. Although it is based on different
+assumptions, the adaptive foraging theory of food web structure
+\parencite{Petchey2008b} provides comparable predictions
+\parencite{Williams2010}. One major recent breakthrough in food web theory have
+been the attempts to parameterize the niche model and other food web models from
+field data and to compare their fit through likelihood methods
+\parencite{Allesina2008, Williams2010, Williams2011}. These methods provide, for
+each species of the food web, the optimal parameters to fit the empirical web
+structures, given the hypothesized underlying rules of the niche model.
 
-Despite their theoretical interest, these methods however come with several drawbacks when comes the time to perform biodiversity scenarios.
-Firstly, they are difficult to apply at large scale because of the technical and logistical requirements of metaweb data collection.
-Secondly, once the model is parameterized, it could only be used to infer feeding interactions between species with already documented interactions (i.e.
-it is impossible to infer potential interactions among species that do never co-occurred).
-Finally, the model optimization is a serious challenge for large datasets with a large number of parameters to evaluate and rough likelihood surfaces.
-There is consequently an urgent need for a method that could rapidly and easily provide an estimate of potential interactions in a metaweb based on incomplete data.
+Despite their theoretical interest, these methods however come with several
+drawbacks when comes the time to perform biodiversity scenarios. Firstly, they
+are difficult to apply at large scale because of the technical and logistical
+requirements of metaweb data collection. Secondly, once the model is
+parameterized, it could only be used to infer feeding interactions between
+species with already documented interactions (i.e. it is impossible to infer
+potential interactions among species that do never co-occurred). Finally, the
+model optimization is a serious challenge for large datasets with a large number
+of parameters to evaluate and rough likelihood surfaces. There is consequently
+an urgent need for a method that could rapidly and easily provide an estimate of
+potential interactions in a metaweb based on incomplete data.
 
-In this paper, we present a method designed to infer the potential interactions between all pairs of species of a species pool (the metaweb) based on observations of body size of predators and their prey.
-We do so by a parameterization of the niche model, based on the well-documented allometric scaling relationship between predator and prey \parencite{Cohen2003, Brose2006, Riede2010}.
-We first develop the method and apply it to food webs from various environments.
-We find the method accurately predicts the interactions (and lack thereof), and that the accuracy increases with the strength of the predator-prey body size relationship.
-We then analyze the sensitivity of the method to incomplete data (missing links) and find that it is robust to sampling effort.
-We finally illustrate the potential of the method to infer the metaweb structure of pelagic fishes of the Meditarrannean sea and the consequences of alteration of body size distribution by global changes or anthropic forcings.
+In this paper, we present a method designed to infer the potential interactions
+between all pairs of species of a species pool based on observations of body
+size of predators and their prey. The method applies to both the local and the
+metaweb scales. We do so by a parameterization of the niche model, based on the
+well-documented allometric scaling relationship between predator and prey
+\parencite{Cohen2003, Brose2006, Riede2010}. We first develop the method and
+apply it to food webs from various environments. We find the method accurately
+predicts the interactions (and lack thereof), and that the accuracy increases
+with the strength of the predator-prey body size relationship. We then analyze
+the sensitivity of the method to incomplete data (missing links) and find that
+it is robust to sampling effort. We finally illustrate the potential of the
+method to infer the metaweb structure of pelagic fishes of the Meditarrannean
+sea and the consequences of alteration of body size distribution by global
+changes or anthropic forcings. The method is best suited for strongly
+size-structured food webs and will likely not hold for other types of
+non-body-size structured interactions. We therefore conclude on the future
+issues to generalize this approach to other types of trait matching models.
 
@@
 
-The method aims to infer the potential interactions among a pool of species from a subset of observations of predator-prey interactions.
-The method follows the following steps, with details provided below:
+The method aims to infer the potential interactions among a pool of species from
+a subset of observations of predator-prey interactions. The method follows the
+following steps, with details provided below:
 \begin{description}
@@
 The niche model predicts the food web structure from a set of three
-species-specific parameters \parencite{Williams2000}: the niche position $n_i$, the feeding niche optimum
-$c_i$ (called the centroid), and the feeding range $r_i$. A species $i$ will
-predate all species $j$ whose niche position $n_j$ lies within the interval
-$[c_i-r_i/2,c_i+r_i/2]$ (Fig. 1). We evaluate all of these parameters from the
-predator-prey body size relationship, enabling us to parameterize the metaweb
-from \emph{observed} interactions only. The parameterization is robust to the
-sampling effort, as it is much easier to document interactions than their
-absence \parencite{Martinez1999}. Our approach is however mostly limited to
-predatory interactions since the body size relationship between herbivores and
-primary producers is not as general \parencite{Riede2010}, and obviously do not
-hold for parasitic, mutualistic, or competitive networks.
+species-specific parameters \parencite{Williams2000}: the niche position $n_i$,
+the feeding niche optimum $c_i$ (called the centroid), and the feeding range
+$r_i$. A species $i$ will predate all species $j$ whose niche position $n_j$
+lies within the interval $[c_i-r_i/2,c_i+r_i/2]$ (Fig. 1). We evaluate all of
+these parameters from the predator-prey body size relationship, enabling us to
+parameterize the metaweb from \emph{observed} interactions only. The
+parameterization is robust to the sampling effort, as it is much easier to
+document interactions than their absence \parencite{Martinez1999}. Our approach
+is however mostly limited to predatory interactions since the body size
+relationship between herbivores and primary producers is not as general
+\parencite{Riede2010}, and obviously do not hold for parasitic, mutualistic, or
+competitive networks.
 
@@
 quantile regressions between $\mathrm{log}_{10}(M_{prey})$ and
-$\mathrm{log}_{10}(M_{pred})$ (the dotted lines at Fig. 1, see the example at Fig.
-2). We note them as $r_{low,i}$ and $r_{high,j}$ respectively, and the
-corresponding parameters $\beta_{0,low/high}$ and $\beta_{1,low/high}$.  In sum,
-the parameter $n_i$ for any species of the metaweb is given by the standardized
-value of the log body size $M_i$, $c_i$ is estimated from the linear regression
-between predator and prey log body size and $r_i$ from the quantile regressions.
+$\mathrm{log}_{10}(M_{pred})$ (the dotted lines at Fig. 1, see the example at
+Fig. 2). We note them as $r_{low,i}$ and $r_{high,j}$ respectively, and the
+corresponding parameters of the linear quantile regresions are
+$\beta_{0,low/high}$ and $\beta_{1,low/high}$. In sum, the parameter $n_i$ for
+any species of the metaweb is given by the standardized value of the log body
+size $M_i$, $c_i$ is estimated from the linear regression between predator and
+prey log body size and $r_i$ from the quantile regressions. Type I regressions
+were used because there is no equivalence of type II models for quantile
+regressions.
 
-The next step of the methodology is to reconstruct the metaweb.
-Once these parameters are calculated from a subsample of species from the regional pool, the coefficients of the different linear models are used to infer the niche parameters of each species of the species pool.
-Again, the niche parameter for any species $i$, $n_i$, is given by the log of body size.
-The centroid of the niche is obtained by the relationship $c_i = \alpha_0 + \alpha_1\times\mathrm{n_i}$, the lower boundary of the niche is $r_{low,i} = \beta_{0,low} + \alpha_{1,low}\times\mathrm{n_i}$ and the upper boundary $r_{high,i} = \beta_{0,high} + \alpha_{1,high}\times\mathrm{n_i}$.
-A feeding link from species $j$ to species $i$ occurs if $n_j > r_{low,i} \& n_j < r_{high,i}$.
-We provide an example at Fig.
-2.
+The next step of the methodology is to reconstruct the metaweb. Once these
+parameters are calculated from a subsample of species from the regional pool,
+the coefficients of the different linear models are used to infer the niche
+parameters of each species of the species pool. Again, the niche parameter for
+any species $i$, $n_i$, is given by the log of body size. The centroid of the
+niche is obtained by the relationship $c_i = \alpha_0 +
+\alpha_1\times\mathrm{n_i}$, the lower boundary of the niche is $r_{low,i} =
+\beta_{0,low} + \alpha_{1,low}\times\mathrm{n_i}$ and the upper boundary
+$r_{high,i} = \beta_{0,high} + \alpha_{1,high}\times\mathrm{n_i}$. A feeding
+link from species $j$ to species $i$ occurs if $n_j > r_{low,i} \& n_j <
+r_{high,i}$. We provide an example at Fig. 2.
 
@@
 We illustrate the method with the food web datasets of Brose et al.
-\parencite{Brose2005}.
-The meta-analysis of Brose \parencite{Brose2006} was conducted on this dataset to test the generality of the predator-prey body size relationship across different systems (terrestrial, aquatic and marine).
-The relationship was found to be very strong across all systems despite exhibiting variability from one to another.
-Each web has between 26 and 380 species and 18 and 1466 feeding links.
-Several of these webs are repetitions over time at a single location, in which cases we pooled the data for each of the 15 different locations to calculate the predator-prey body size relationship.
-We removed 4 datasets that had a non-significant predator-prey relationship and were thus useless with our approach.
-The links are not systematically sampled, meaning that any absence of a link between two species for a given dataset could either be a real absence or due to insufficient sampling or lack of information.
-While the predator-prey body size relationship is very strong over all datasets (Brose2006), there is quite substantial variation among them, enabling us to assess the sensitivity of the method to the strength of this relationship.
+\parencite{Brose2005}. The meta-analysis of Brose \parencite{Brose2006} was
+conducted on this dataset to test the generality of the predator-prey body size
+relationship across different systems (terrestrial, aquatic and marine). The
+relationship was found to be very strong across all systems despite exhibiting
+variability from one to another. Each web has between 26 and 380 species and 18
+and 1466 feeding links. Several of these webs are repetitions over time at a
+single location, in which cases we pooled the data for each of the 15 different
+locations to calculate the predator-prey body size relationship. We removed 4
+datasets that had a non-significant predator-prey relationship and were thus
+useless with our approach. The links are not systematically sampled, meaning
+that any absence of a link between two species for a given dataset could either
+be a real absence or due to insufficient sampling or lack of information. While
+the predator-prey body size relationship is very strong over all datasets
+(Brose2006), there is quite substantial variation among them, enabling us to
+assess the sensitivity of the method to the strength of this relationship.
 
-We assessed the performance of our method using the True Skill Statistic ($TSS$).
-The $TSS$ is based on the partition of events (the prediction of a trophic interaction) between four components: the component $a$ reports the number of links that are both predicted and observed, $b$ reports predicted links with no corresponding observation, $c$ reports the number of observed links that are  predicted absent, and $d$ reports the number of predicted and observed absences of links.
-The TSS is then calculated as $TSS =(ad-bc)/\left[(a+c)(b+d)\right]$.
-The $TSS$ quantifies the proportion of prediction success relative to false predictions and returns values ranging between 1 (perfect predictions) and -1 (inverted forecast) \parencite{Allouche2006}.
+We assessed the performance of our method using the True Skill Statistic
+($TSS$). The $TSS$ is based on the partition of events (the prediction of a
+trophic interaction) between four components: the component $a$ reports the
+number of links that are both predicted and observed, $b$ reports predicted
+links with no corresponding observation, $c$ reports the number of observed
+links that are predicted absent, and $d$ reports the number of predicted and
+observed absences of links. The TSS is then calculated as $TSS
+=(ad-bc)/\left[(a+c)(b+d)\right]$. The $TSS$ quantifies the proportion of
+prediction success relative to false predictions and returns values ranging
+between 1 (perfect predictions) and -1 (inverted forecast)
+\parencite{Allouche2006}.
 
-We calculated the $TSS$ for each of the 11 different webs and related it to the strength of the predator-prey body size relationship, measured by the $R^2$ of the linear model.
-We find that the $TSS$ is positive for all webs, ranging from 0.13 to 0.76 (Fig.
-3A).
-We find a positive relationship between the $R^2$ of the linear model and the $TSS$ ($R^2=0.50$, $p=0.016$).
-When we decompose the different components of predictions and observations, we find that the fraction of prediction match is high, with an average of $(\overline{a}+\overline{d})/{S^2}=0.58$, Fig.
-3B).
-The fraction of wrong predictions is lower, at $\overline{b+c}/S^2=0.40$, and decreases with the $R^2$ of the predator-prey body size relationship.
+We calculated the $TSS$ for each of the 11 different webs and related it to the
+strength of the predator-prey body size relationship, measured by the $R^2$ of
+the linear model. We find that the $TSS$ is positive for all webs, ranging from
+0.13 to 0.76 (Fig. 3A). We find a positive relationship between the $R^2$ of the
+linear model and the $TSS$ ($R^2=0.50$, $p=0.016$). When we decompose the
+different components of predictions and observations, we find that the fraction
+of prediction match is high, with an average of
+$(\overline{a}+\overline{d})/{S^2}=0.58$, Fig. 3B). The fraction of wrong
+predictions is lower, at $\overline{b+c}/S^2=0.40$, and decreases with the $R^2$
+of the predator-prey body size relationship.
 
-The parameterized niche model tends to overestimate the number of links in a web (see the example at Fig.
-2).
-This result is significant but not surprising, given that these datasets do not necessarily contain all links, as they were not designed with this purpose, and thus some of the links might have been missed.
-This interpretation is also reminiscent of previous debates on the difficulty to sample all links in a web \parencite{Martinez1999}.
-It is also well known that the niche model predicts a continuous diet along the niche axis (the webs are said to be interval \parencite{Cohen1990, Stouffer2006}), while real food webs do not have this characteristic.
-We thus might over predict link density within the niche of a given species.
-Previous studies \parencite{Allesina2008} and the Application 1 however show this problem is easily circumvented when a second niche axis, \emph{e.g.} an environmental niche, comes into play.
-A recent study on dimensionality of networks shown that most webs have between 3 and 7 dimensions \parencite{Eklof2013}, meaning that adding a few more niche axes can greatly improve the accuracy of predictions.
+The parameterized niche model tends to overestimate the number of links in a web
+(see the example at Fig. 2). This result is significant but not surprising,
+given that these datasets do not necessarily contain all links, as they were not
+designed with this purpose, and thus some of the links might have been missed.
+This interpretation is also reminiscent of previous debates on the difficulty to
+sample all links in a web \parencite{Martinez1999}. It is also well known that
+the niche model predicts a continuous diet along the niche axis (the webs are
+said to be interval \parencite{Cohen1990, Stouffer2006}), while real food webs
+do not have this characteristic. We thus might over predict link density within
+the niche of a given species. Previous studies \parencite{Allesina2008} and the
+Application 1 however show this problem is easily circumvented when a second
+niche axis, \emph{e.g.} an environmental niche, comes into play. A recent study
+on dimensionality of networks shown that most webs have between 3 and 6
+dimensions \parencite{Eklof2013}, meaning that adding a few more niche axes can
+greatly improve the accuracy of predictions.
 
@@
 \subsection{Sensitivity to sampling effort}
-We subsequently explored the impact of sampling effort on the accuracy of the model predictions.
-We assumed a random subsampling of all the interactions occurring in the food web.
-To do so, we selected a species rich food web ($S = 67$) from the Brose et al.
-dataset, with 601 observed feeding links and a good $TSS$ (0.51).
-We randomly removed from 0 to $90\%$ of the observed links to do the evaluation of the parameters of the linear regressions (i.e.
-e decrease the quantity of information used to calibrate the model).
-We then after compared the empirical web (with all species) to the inferred web with these parameters (all species also).
-The comparison was done again with the TSS.
-We performed 100 randomizations per number of removed links.
-This numerical simulation reproduces incomplete sampling in the process of building the food web.
-We find that the $TSS$ remains constant up until $80\%$ of the observed links are removed (Fig.
-3).
-At this level, the $TSS$ starts to decline drastically and its variance increases.
+We subsequently explored the impact of sampling effort on the accuracy of the
+model predictions. We assumed a random subsampling of all the interactions
+occurring in the food web. To do so, we selected a species rich food web ($S =
+67$) from the Brose et al. dataset, with 601 observed feeding links and a good
+$TSS$ (0.51). We randomly removed from 0 to $90\%$ of the observed links to do
+the evaluation of the parameters of the linear regressions (i.e. e decrease the
+quantity of information used to calibrate the model). We then after compared the
+empirical web (with all species) to the inferred web with these parameters (all
+species also). The comparison was done again with the TSS. We performed 100
+randomizations per number of removed links. This numerical simulation reproduces
+incomplete sampling in the process of building the food web. We find that the
+$TSS$ remains constant up until $80\%$ of the observed links are removed (Fig.
+3). At this level, the $TSS$ starts to decline drastically and its variance
+increases.
 
-This result shows that our method of parameterization of the niche model is robust with regard to sampling effort.
-Note however that a biased sampling with respect to body size (e.g.
-sampling of the largest species) might be more likely to reduce the fit of the predator-prey body size relationship.
-The aggregation intro trophic species that do have the same body size and the same diet should not impact the prediction since it will not affect parameter evaluation.
-It will however reduce the fit of the predator-prey body size relationship and therfore the accuracy of the method if the species do have different body sizes.
-The same artifact will be observed if there is strong intraspecific variation in body size (see the Discussion).
+This result shows that our method of parameterization of the niche model is
+robust with regard to sampling effort. Note however that a biased sampling with
+respect to body size (e.g. sampling of the largest species) might be more likely
+to reduce the fit of the predator-prey body size relationship. The aggregation
+intro trophic species that do have the same body size and the same diet should
+not impact the prediction since it will not affect parameter evaluation. It will
+however reduce the fit of the predator-prey body size relationship and therfore
+the accuracy of the method if the species do have different body sizes. The same
+artifact will be observed if there is strong intraspecific variation in body
+size (see the Discussion).
 
@@
 \subsection{Dataset}
-We now present an application of the method to infer the metaweb of interactions among fishes of the Mediterranean sea.
-The Mediterranean is known as a hotspot of fish diversity that is severely threatened by climate change and overfishing \parencite{Mouillot2011}.There are 557 fish species in the regional pool, with a maximum body size ranging from 2.3 cm to 1100 cm \parencite{Whithead1986, Louisy2005, Froese2011}.
-Chondrichthyans, mammals and turtles were under represented in the two trophic networks and were removed from the analyses.
-We parameterized the niche model with a subset of species, from two different highly resolved food webs from the Catalan area \parencite{Coll2006} (82 species) and Corsica \parencite{Albouy2010} (58 species).
+We now present an application of the method to infer the metaweb of interactions
+among fishes of the Mediterranean sea. The Mediterranean is known as a hotspot
+of fish diversity that is severely threatened by climate change and overfishing
+\parencite{Mouillot2011}.There are 557 fish species in the regional pool, with a
+maximum body size ranging from 2.3 cm to 1100 cm \parencite{Whithead1986,
+Louisy2005, Froese2011}. Chondrichthyans, mammals and turtles were under
+represented in the two trophic networks and were removed from the analyses. We
+parameterized the niche model with a subset of species, from two different
+highly resolved food webs from the Catalan area \parencite{Coll2006} (82
+species) and Corsica \parencite{Albouy2010} (58 species).
 
 \subsection{Inferring the metaweb for Mediterrannean fishes}
-We estimated parameters $n$, $c$ and $r$ for each of the 557 species and inferred the potential interactions among all of them (the example in the Supplementariy code is based on this dataset).
-The metaweb has a total of 126 501 links, for a connectance of 0.41 (Fig.
-5A).
-The metaweb is also highly nested (specialist species feed on a subset of prey of the most generalist species.
-Fig.
-5A).
-We also considered a second niche axis related to species spatial distribution.
-Most fish species have restricted geographic range within the Mediterranean sea because of specific response to temperature and other environmental variables \parencite{Albouy2012}.
-We therefore removed from the metaweb all links between species having no range overlap.
-Data on the extent of occurrence of fish species were compiled from a published atlas of fishes of the northern Atlantic and the Mediterranean \parencite{Whitehead1986}.
-This atlas is based on regional data sets and expert knowledge and was edited between 1984 and 1986.
-It currently provides the only available basin-wide information on the extent of occurrence of all Mediterranean Sea fish species.
-The above mentioned atlas do not account for the bathymetric distribution of Mediterranean fish species, yet bathymetry is considered as one of the main factors accounting for marine fish distributions \parencite{Louisy2005}.
-We therefore refined the extent of occurrence maps by clipping off areas with depths that fall outside the minimum or maximum known for the species.
-Species' bathymetric ranges were obtained from FishBase \parencite{Froese2010, Louisy2005}.
-The resulting metaweb has a total of 95 989 links, for a connectance of $C = 0.31$.
-Connectance decreases because links are removed by incomptabilities in bathymetry but the total number of species stays constant.
-This metaweb is clearly less interval (Fig.
-5B).
-Contiguous gaps in the diet are likely to emerge from modularity in the co-occurrence matrix \parencite{Araujo2011}.
-Future studies should explore how co-occurrence is constraining the topological structure of metawebs.
+We estimated parameters $n$, $c$ and $r$ for each of the 557 species and
+inferred the potential interactions among all of them (the example in the
+Supplementariy code is based on this dataset). The metaweb has a total of 126
+501 links, for a connectance of 0.41 (Fig. 5A). The metaweb is also highly
+nested (specialist species feed on a subset of prey of the most generalist
+species. Fig. 5A). We also considered a second niche axis related to species
+spatial distribution. Most fish species have restricted geographic range within
+the Mediterranean sea because of specific response to temperature and other
+environmental variables \parencite{Albouy2012}. We therefore removed from the
+metaweb all links between species having no range overlap. Data on the extent of
+occurrence of fish species were compiled from a published atlas of fishes of the
+northern Atlantic and the Mediterranean \parencite{Whitehead1986}. This atlas is
+based on regional data sets and expert knowledge and was edited between 1984 and
+1986. It currently provides the only available basin-wide information on the
+extent of occurrence of all Mediterranean Sea fish species. The above mentioned
+atlas do not account for the bathymetric distribution of Mediterranean fish
+species, yet bathymetry is considered as one of the main factors accounting for
+marine fish distributions \parencite{Louisy2005}. We therefore refined the
+extent of occurrence maps by clipping off areas with depths that fall outside
+the minimum or maximum known for the species. Species' bathymetric ranges were
+obtained from FishBase \parencite{Froese2010, Louisy2005}. The resulting metaweb
+has a total of 95 989 links, for a connectance of $C = 0.31$. Connectance
+decreases because links are removed by incomptabilities in bathymetry but the
+total number of species stays constant. This metaweb is clearly less interval
+(Fig. 5B). Contiguous gaps in the diet are likely to emerge from modularity in
+the co-occurrence matrix \parencite{Araujo2011}. Future studies should explore
+how co-occurrence is constraining the topological structure of metawebs.
 
@@
 \subsection{Impact of global changes}
-Our method to parameterize the niche model has a unique feature relative to the original niche model \parencite{Williams2000}: the network properties of the original model, such as the number of links, food chain length and degree distribution (the number of in and out feeding links per species), are controlled by the input parameters (species richness and connectance), wherea all properties of our parameterized niche model are emergent features of the predator-prey body size relationship and the frequency distribution of body size.
-The connectance in the niche model is fixed by the user; in our case it strongly depends on the scaling of the feeding range with body size and the frequency of larger body species.
+Our method to parameterize the niche model has a unique feature relative to the
+original niche model \parencite{Williams2000}: the network properties of the
+original model, such as the number of links, food chain length and degree
+distribution (the number of in and out feeding links per species), are
+controlled by the input parameters (species richness and connectance), wherea
+all properties of our parameterized niche model are emergent features of the
+predator-prey body size relationship and the frequency distribution of body
+size. The connectance in the niche model is fixed by the user; in our case it
+strongly depends on the scaling of the feeding range with body size and the
+frequency of larger body species.
 
-This feature is particularly important to understand global change impacts on community structure.
-For instance, a common prediction of the impact of fisheries on the body size distribution is the reduction in the average and variance of body size \parencite{Jackson2001}.
-Similarly, global warming is also expected to alter fish body size distribution towards smaller species \parencite{Cheung2012}.
-We explored by simulations the impact of these changes on the degree distribution of the Mediterranean metaweb.
-Results are illustrated at Fig.
-6.
-The shape of the cumulative degree distribution provides a visual assessment of the distribution of diet specificity in a network.
-The curves becomes steeper and the fall moves to the left with increasing specialization (indicative of a larger proportion of species with a low degree).
-Even if the simulated scenarios are crude representations of the predicted alterations of community structure, they both show that fisheries impacts on body size will substantially alter the network properties.
-The results at Fig.
-6 show that reduction in the average body size will decrease the average number of preys per predator (there is an initial sharper decline of the cumulative distribution), but that super generalist species will also appear (because of the shift of the tail toward the right).
-The removal of the 40\% largest species reduces much more the average generality which is expected as larger species are predators with a large feeding niche in the niche model.
-The two scenarios consequently increases substantially the relative abundance of species with a smaller degree, even for the average size reduction scenario where the total number of species is held constant.
-The change in the degree distribution is likely to reduce substantially the expected persistence and stability of these communities \parencite{Gravel2011a, Gravel2011b}.
+This feature is particularly important to understand global change impacts on
+community structure. For instance, a common prediction of the impact of
+fisheries on the body size distribution is the reduction in the average and
+variance of body size \parencite{Jackson2001}. Similarly, global warming is also
+expected to alter fish body size distribution towards smaller species
+\parencite{Cheung2012}. We explored by simulations the impact of these changes
+on the degree distribution of the Mediterranean metaweb. Results are illustrated
+at Fig. 6. The shape of the cumulative degree distribution provides a visual
+assessment of the distribution of diet specificity in a network. The curves
+becomes steeper and the fall moves to the left with increasing specialization
+(indicative of a larger proportion of species with a low degree). Even if the
+simulated scenarios are crude representations of the predicted alterations of
+community structure, they both show that fisheries impacts on body size will
+substantially alter the network properties. The results at Fig. 6 show that
+reduction in the average body size will decrease the average number of preys per
+predator (there is an initial sharper decline of the cumulative distribution),
+but that super generalist species will also appear (because of the shift of the
+tail toward the right). The removal of the 40\% largest species reduces much
+more the average generality which is expected as larger species are predators
+with a large feeding niche in the niche model. The two scenarios consequently
+increases substantially the relative abundance of species with a smaller degree,
+even for the average size reduction scenario where the total number of species
+is held constant. The change in the degree distribution is likely to reduce
+substantially the expected persistence and stability of these communities
+\parencite{Gravel2011a, Gravel2011b}.
 
@@
 
-In this paper, we presented a method to infer potential interactions among an arbitrary pool of species.
-The data required to perform this methodology are simple to obtain, as the body size of a large number of species are available from reference databases, or easy to measure.
-Because we rely on a robust allometric relationship, applying this method requires neither complex statistical techniques, nor an exhaustive knowledge of the realized interactions within the metaweb of interest.
-In addition to the opportunity to simulate biodiversity scenarios, our method can also help generating baseline expectations about the food web structure for environments which are notoriously difficult to sample, such as soils, deep-sea environments, or fossil records.
-However, because this allometric relationship is characteristic of predatory interactions, our method will likely not hold for other types of non-body-size structured interactions such as herbivory and parasitism.
+In this paper, we presented a method to infer potential interactions among an
+arbitrary pool of species. The data required to perform this methodology are
+simple to obtain, as the body size of a large number of species are available
+from reference databases, or easy to measure. Because we rely on a robust
+allometric relationship, applying this method requires neither complex
+statistical techniques, nor an exhaustive knowledge of the realized interactions
+within the metaweb of interest. In addition to the opportunity to simulate
+biodiversity scenarios, our method can also help generating baseline
+expectations about the food web structure for environments which are notoriously
+difficult to sample, such as soils, deep-sea environments, or fossil records.
+However, because this allometric relationship is characteristic of predatory
+interactions, our method will likely not hold for other types of non-body-size
+structured interactions such as herbivory and parasitism.
 
-Ontogenic shifts in diet are common in many size-structured populations and could be accounted for in two ways with this methodology.
-First, they will enter the model parameterization by simply including a link from species A (the largest) to species B (the smallest), and the opposite.
-This would yield in a data point for species B figuring above the 1:1 relationship.
-Such a data point will obviously influence the model calibration and enlarge the regime of all species.
-It is not obvious however that ontogenic shifts will be found in the metaweb as it would require an upper limit of the range above the 1:1 relationship.
-The alternative approach would be to distinguish "sub-species" by size categories in the model calibration and then in the reconstruction of the metaweb.
-This approach would force ontogenic shifts and perhaps more precisely represent the interaction matrix where the within-population size structure is important.
+It appears at Fig. 2 that the feeding range increases with the body size of the
+predator. This result was quite general across datasets with a good fit of the
+predator-prey body size relationship, although with considerable variation in
+the slope of the relationship. It offers the possibility to compare empirical
+based estimates of the parameters to the original niche model of
+\textcite{Williams2000}. For this specific dataset that the model for the
+centroid is $c_i = -1.34 + 0.66n_i$ and the average range
+($\overline{r}_i=(r_{high,i} - r_{low,i})/2$) is $\overline{r}_i = 0.63 +
+0.78n_i$. The original niche models assumed that $r_i$ scales linearly with
+connectance $C$ and the niche position, such that $r_i = 2Cn_i$. Even though the
+parameterization suggests a linear increase of generality with body size, the
+final number of preys in the diet for a given size will depend on the frequency
+distribution of body size. A large predator for instance could have a large
+feeding range, but only few species to find on and effectively appears as a
+specialist. This relationship will have to be investigated further, among
+several food webs (e.g. \textcite{Digel2011}), because the scaling of generality
+with trophic rank has several consequences on persistence
+\parencite{Gravel2011b} and food web dynamics \parencite{Brose2006,Berlow2009}.
 
-The method should be completed with other sources of informations to better predict gaps in the interaction matrix.
-The original niche model was definitely inspired by the predator-prey body size relationship, but was intented to be more general and eventually deal with several niche axes \parencite{Williams2000}.
-\textcite{Allesina2008} indeed found that adding a second axis, creating gaps into the first axis interaction matrix, increases the fit of the model to empirical data.
-It also makes the network less interval (a continuous succession of species diets along the niche axis), a structural issue of the niche model that was reported by \textcite{Cattin2004} and \textcite{Bersier2006}.
-There are numerous sources of information that could be used to improve the model, such as co-occurrence and functional traits.
+Ontogenic shifts in diet are common in many size-structured populations and
+could be accounted for in two ways with this methodology. First, they will enter
+the model parameterization by simply including a link from species A (the
+largest) to species B (the smallest), and the opposite. This would yield in a
+data point for species B figuring above the 1:1 relationship. Such a data point
+will obviously influence the model calibration and enlarge the regime of all
+species. It is not obvious however that ontogenic shifts will be found in the
+metaweb as it would require an upper limit of the range above the 1:1
+relationship. The alternative approach would be to distinguish "sub-species" by
+size categories in the model calibration and then in the reconstruction of the
+metaweb. This approach would force ontogenic shifts and perhaps more precisely
+represent the interaction matrix where the within-population size structure is
+important.
 
-Our application with the Mediterannean pelagic fish food web provides an example of how straightforward it is to add additional information so as to improve the parameterization.
-A similar approach could also build on the comptability of other traits such as phenology, location in the water column or hunting modes.
-While the approach we describe here is based on very simple statistics, the next methodological efforts will also have to take into account more various and heterogeneous sources of data such as phylogeny \parencite{Eklof2012} and expert knowledge.
-Bayesian inference appears a good candidate to achieve this goal with the possibility to constrain the prior distribution of parameters for each species.
+The method should be completed with other sources of informations to better
+predict gaps in the interaction matrix. The original niche model was definitely
+inspired by the predator-prey body size relationship, but was intented to be
+more general and eventually deal with several niche axes
+\parencite{Williams2000}. \textcite{Allesina2008} indeed found that adding a
+second axis, creating gaps into the first axis interaction matrix, increases the
+fit of the model to empirical data. It also makes the network less interval (a
+continuous succession of species diets along the niche axis), a structural issue
+of the niche model that was reported by \textcite{Cattin2004} and
+\textcite{Bersier2006}. There are numerous sources of information that could be
+used to improve the model, such as co-occurrence and functional traits.
 
-Adding this method to the ecologist's toolbox is a timely issue because there is an urgent need to include interactions into future biodiversity scenarios \parencite{Thuiller2013}.
-There has been impressive progress in biogeography over the last fifteen years to predict the impact of global changes on range shifts, extinction risks, and the future distribution of biodiversity, but we now face the realization that emerging ecosystems are unlikely to be a spatial displacement of the ones we currently know.
-This method will help assessing global change impacts of community structure, moving the field of biogeography closer to ecosystem functioning.
+Our application with the Mediterannean pelagic fish food web provides an example
+of how straightforward it is to add additional information so as to improve the
+parameterization. A similar approach could also build on the comptability of
+other traits such as phenology, location in the water column or hunting modes.
+While the approach we describe here is based on very simple statistics, the next
+methodological efforts will also have to take into account more various and
+heterogeneous sources of data such as phylogeny \parencite{Eklof2012} and expert
+knowledge. Bayesian inference appears a good candidate to achieve goal. It
+offers the possibility to constrain the prior distribution of the likelihood of
+any pairwise interaction, based on trait matching, using alternative source of
+data. The method we employed here was based on the match between predator and
+prey traits. This method could be generalized by looking at the match between
+all potential traits. \textcite{Eklof2013} indeed found that the match between
+only three traits is enough to encompass a vast majority of interactions. But
+when such data is not always available, then it might be possible to use
+phylogeny as a proxy for a high dimensional trait species, provided that traits
+are conserved along the phylogeny \parencite{Mouquet2012}. A bayesian addition
+to the model would be to weight the likelihood that species $j$ is a predator of
+species $i$, considering that the closest relative of this predator is also a
+predator of $i$. It could account for part of the unexplained variation we found
+in our analysis, for instance by constraining the range of the diet for some
+large predators or by creating holes within the feeding range
+\parencite{Rall2011}.
+
+Adding this method to the ecologist's toolbox is a timely issue because there is
+an urgent need to include interactions into future biodiversity scenarios
+\parencite{Thuiller2013}. There has been impressive progress in biogeography
+over the last fifteen years to predict the impact of global changes on range
+shifts, extinction risks, and the future distribution of biodiversity, but we
+now face the realization that emerging ecosystems are unlikely to be a spatial
+displacement of the ones we currently know. This method will help assessing
+global change impacts of community structure, moving the field of biogeography
+closer to ecosystem functioning.
 
 \section{Acknowledgements}
-We thank I. Gounand for preparing the food web data. DG received financial support from NSERC and Canada Research Chair program. TP is funded by a MELS-FQRNT post-doctoral fellowship.
+We thank I. Gounand for preparing the food web data. We also thank N. Martinez,
+U. Brose and two anonymous reviewers for their constructive comments and
+stimulating discussion. DG received financial support from NSERC and Canada
+Research Chair program. TP is funded by a MELS-FQRNT post-doctoral fellowship.
 \newpage
@@
 \subsection*{Figure 1} 
-Schematic representation of the niche model and its application to the predator-prey body size relationship.
-Three consumer species are represented.
-The white triangles correspond to the niche position of predators (their position on the X axis is transposed along the Y axis).
-For most cases, prey size is smaller that the predator size and thus fall under the 1:1 relationship.
-In some occasions, however, the feeding range can overlay the 1:1 relationship, for instance in presence of ontogenic shifts in diet.
-For a given predator, we consider that the niche centroid ($c_i$) is the average prey size, given by the linear relationship between predator and prey size (black line).
-The boundaries of the feeding range ($r_i$) are given by the 5\% and 95\% quantile regression lines (dotted lines).
-A predator feeds on all prey species which their niche lies between these boundaries.
-In this specific example, the largest predator feeds on the two smaller species (the white triangles depicting the niche lies between range boundaries) and the intermediate size predator feeds on the smallest species.
+Schematic representation of the niche model and its
+application to the predator-prey body size relationship. Three consumer species
+are represented. The white triangles correspond to the niche position of
+predators (their position on the X axis is transposed along the Y axis). For
+most cases, prey size is smaller that the predator size and thus fall under the
+1:1 relationship. In some occasions, however, the feeding range can overlay the
+1:1 relationship, for instance in presence of ontogenic shifts in diet. For a
+given predator, we consider that the niche centroid ($c_i$) is the average prey
+size, given by the linear relationship between predator and prey size (black
+line). The boundaries of the feeding range ($r_i$) are given by the 5\% and 95\%
+quantile regression lines (dotted lines). A predator feeds on all prey species
+which their niche lies between these boundaries. In this specific example, the
+largest predator feeds on the two smaller species (the white triangles depicting
+the niche lies between range boundaries) and the intermediate size predator
+feeds on the smallest species.
 
 \subsection*{Figure 2} 
-Example of predator-prey body size relationship and predictions from the parameterized niche model.
-Open dots represent observed links while black dots are predicted interactions based on the parameterization of the niche model.
-The bullseye symbols thus correspond to a match between predicted occurrence of a link and the real data (the "a" classification in the calculation of the TSS, see main text), a black dot a predicted link with not observation ("b") and an open circle a non-predicted and observed link ("c").
+Example of predator-prey body size relationship and
+predictions from the parameterized niche model. Open dots represent observed
+links while black dots are predicted interactions based on the parameterization
+of the niche model. The bullseye symbols thus correspond to a match between
+predicted occurrence of a link and the real data (the "a" classification in the
+calculation of the TSS, see main text), a black dot a predicted link with not
+observation ("b") and an open circle a non-predicted and observed link ("c").
 Data from a creek bed located in Australia \parencite{Brose2005}.
@@
 \subsection*{Figure 3} 
-Performance of the parameterized niche model to predict food web structure for the 11 food webs.
-A) Relationship between the TSS and the $R^2$ of the predator-prey body size relationship.
-B) Partitionning of the different components of the TSS.
+Performance of the parameterized niche model to predict
+food web structure for the 11 food webs. A) Relationship between the TSS and the
+$R^2$ of the predator-prey body size relationship. B) Partitionning of the
+different components of the TSS.
 
 \subsection*{Figure 4} 
-Effect of the sampling effort on the accuracy of the parameterized niche model to predict food web structure. The simulation was conducted with the same data as Fig. 2.
+Effect of the sampling effort on the accuracy of the
+parameterized niche model to predict food web structure. The simulation was
+conducted with the same data as Fig. 2.
 
 \subsection*{Figure 5} 
-Illustration of the metaweb of the Mediterannean pelagic fishes (interactions in black).
-Panel A) represents the full metaweb and B) the same metaweb for which links between species not co-occuring together were removed (their range overlap for less than $0.1\%$ of the Mediterannean sea).
+Illustration of the metaweb of the Mediterannean pelagic
+fishes (interactions in black). Panel A) represents the full metaweb and B) the
+same metaweb for which links between species not co-occuring together were
+removed (their range overlap for less than $0.1\%$ of the Mediterannean sea).
 
 \subsection*{Figure 6} 
-Impacts of altering the body size distribution of Meditarrennean fishes on the degree distribution of the metaweb.
-The black line corresponds to the original metaweb degree distribution.
-For the first scenario, we simulated a $40\%$ reduction in average body size and recalculated the metaweb properties, keeping the predator-prey body size relationship constant (dotted line).
-For the second scenario we eliminated the top $40\%$ largest species and recalculated the metaweb properties (dashed line).
+Impacts of altering the body size distribution of
+Meditarrennean fishes on the degree distribution of the metaweb. The black line
+corresponds to the original metaweb degree distribution. For the first scenario,
+we simulated a $40\%$ reduction in average body size and recalculated the
+metaweb properties, keeping the predator-prey body size relationship constant
+(dotted line). For the second scenario we eliminated the top $40\%$ largest
+species and recalculated the metaweb properties (dashed line).
 

### 2013-06-18 replies.tex

@@
 
-\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}
+\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We do agree that using phylogenetic information should help improve the technique much beyond what we actually do.
+This is why we made a mention of this opportunity toward the end of the discussion.
+But it's right we only mentionned it and did not developped our ideas any further.
+We added the following lines (LXXX) to the discussion:}}
+
+\textcolor{blue}{Bayesian inference appears a good candidate to achieve goal.
+It offers the possibility to constrain the prior distribution of the likelihood of any pairwise interaction, based on trait matching, using alternative source of data.
+The method we employed here was based on the match between predator and prey traits.
+This method could be generalized by looking at the match between all potential traits.
+Eklof et al.
+(2013) indeed found that the match between only three traits is enough to encompass a vast majority of interactions.
+But when such data is not always available, then it might be possible to use phylogeny as a proxy for a high dimensional trait species, provided that traits are conserved along the phylogeny (Mouquet et al.
+2012).
+A bayesian addition to the model would be to weight the likelihood that species $j$ is a predator of species $i$, considering that the closest relative of this predator is also a predator of $i$.
+It could account for part of the unexplained variation we found in our analysis, for instance by constraining the range of the diet for some large predators or by creating holes within the feeding range (Rall et al.
+2011).}
 
@@
 
-\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}
+\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{This is certainly an intriguing result coming out from our analysis.
+We also find this result interesting because it links to some of our previous work on persistence in metacommunities and our current work on the biogeography of body size.
+We also had a discussion with Neo Martinez at a previous workshop about this relationship, he was curious to see if his assumption of a linear relationship between the niche and the range of the diet was confirmed (Williams and Martinez, 2000).
+There are already a large number of figures in the paper (6) so we prefer not to add a new one, that could already be guessed from the Fig.
+2.
+We however added the following discussion (at PXLX):}}
+
+\textcolor{blue}{It appears at Fig.
+2 that the feeding range increases with the body size of the predator.
+This result was quite general across datasets with a good fit of the predator-prey body size relationship, although with considerable variation in the slope of the relationship.
+It offers the possibility to compare empirical based estimates of the parameters to the original niche model of Williams (2011).
+For this specific dataset that the model for the centroid is $c_i = -1.34 + 0.66n_i$ and the average range ($\overline{r}_i=(r_{high,i} - r_{low,i})/2$) is $\overline{r}_i = 0.63 + 0.78n_i$.
+The original niche models assumed that $r_i$ scales linearly with connectance $C$ and the niche position, such that $r_i = 2Cn_i$.
+Even though the parameterization suggests a linear increase of generality with body size, the final number of preys in the diet for a given size will depend on the frequency distribution of body size.
+A large predator for instance could have a large feeding range, but only few species to find on and effectively appears as a specialist.
+This relationship will have to be investigated further, among several food webs (e.g.
+Digel et al.
+2011), because the scaling of generality with trophic rank has several consequences on persistence (Gravel et al.
+2011) and food web dynamics (e.g.
+Brose et al.
+2006, Berlow et al.
+2009).}
 
@@
 
-\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}
+\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We fully agree with this result, it was also the central motivation for our investigations in a recent paper by Gravel et al.
+(2011, Ecology Letters).
+We hypothesized that this difference was the result of extinction-colonization dynamics, promoting the persistence of the most generalist species in local communities.
+It is however hard to figure out where to put this result in the current manuscript.
+We are currently working on a theory for metawebs, trying to develop a framework to improve inference of local web structure given the probability of the interactions in the metaweb.
+This approach considers the likelihood of an interaction between a pair of species given their co-occurrence andfavorable environmental conditions.
+This topic is however beyond the topic of the current paper.
+In fact, it goes the other way around.
+We need information on trait-matching to predict potential interactions in the metaweb (the topic of the current ms), and then a theory for sampling the metaweb.}}
 
@@
 
-\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}
+\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We do not find the corresponding point to correct.
+The lines following L214 refer to the paper by Eklof et al., and after a double checking of the paper it was found that most webs had between 3 and 6 dimensions, up to 9.
+We corrected accordingly.}}
 
@@
 working at the local or regional scale. In the text, we give examples at both
-these scales (locally in figures 2 and 3, regionnaly in figure 5). We do agree
+these scales (locally in figures 2 and 3, regionaly in figure 5). We do agree
 with the fact that additional information will make the predictions better; this
@@
 co-occurence along the depth gradient) is pictured in Fig. 5b. This is also
-explicitely written in the discussion (L. XXX-XXX).}}
+explicitly written in the discussion (L. XXX-XXX). We corrected the abstract and the last paragraph of the introduction to make clear that our metholody applies at both the local and metaweb scales.}}
 
@@
 predator body-size. This is the purpose of Fig. 3; this relationship is also
-described in section 3.1 ``Predictive performance''.}}
+described in section 3.1 ``Predictive performance''.
+We made this point clear in the opening paragraph of the Discussion: 'However, because this allometric relationship is characteristic of predatory interactions, our method will likely not hold for other types of non-body-size structured interactions such as herbivory and parasitism'.
+We added also some cautionary remarks in the last paragraph of the introduction: 'The method is best suited for strongly size-structured food webs and will likely not hold for other types of non-body-size structured interactions.
+We therefore conclude on the future issues to generalize this approach to other types of trait matching models'.}}
 
@@
 \medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The study of Rohr et al.
-(2010), does not allow to evaluate the parameters of a new species entering the community, neither the metaweb (which is the object of the current study).
+(2010), does not allow to evaluate the parameters of a new species entering a local community, neither the metaweb (which is the object of the current study).
 It is therefore not possible to infer the potential links an immigrating species will do with the resident species.
@@
 
-\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}
+\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We do agree that the best statistical model for this analysis should be a type 2 regression.
+We however deliberately used a type 1 regression for two reasons: i) we needed the R2 of the model to perform the analysis of predictive performance (Fig.
+3).
+ii) we are not aware of any quantile regression that could account for uncertainty in the independent variable.
+We added a mention to this issue at LXXX.}}
 
@@
 
-\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}
+\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We modified the sentence to avoid amiguities.
+The metaweb gives interactions among a given set of species, wether at local or regional scales.}}
 
@@
 
-\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}
+\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{See the above responses to previous comments.}}
 
@@
 
-\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}
+\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{These are the parameters of the linear quantile regressions. The sentence was corrected accordingly.}}
 
@@
 interesting part of a model is ultimately a matter of personal taste, and
-adequation to the study objectives. Given that (especialyl when no other traits
+adequation to the study objectives. Given that (especialy when no other traits
 than body size are included), this method tends to over-estimate the number of
@@
 \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The choice of quantiles are left free to the user in the R code providing with this article, by default, we chose the most commonly used threshold of 5\% and 95\%.
-}}
+A threshold of 100\% would include all interactions, but would tend to overpredict the link density.}}
 
@@
 %---------------% 
-\medskip Figure 2: An important difference between the
-original and the parameterized niche model is apparent in this figure: here, the
-$c_i$ and $r_i$ are constrained by the allometric regression, which is not the
-case in the original model. From the distribution of the open dots, this appears
-quite problematic in this figure (many open dots are outside the predicted
-range; many predicted interactions are not existing), and this questions the
-usefulness of the whole approach. Other traits may be needed; perhaps performing
-several regressions for different broad taxonomic groups may also improve the
-approach, and widen its applicability.
+\medskip Figure 2: An important difference between the original and the
+parameterized niche model is apparent in this figure: here, the $c_i$ and $r_i$
+are constrained by the allometric regression, which is not the case in the
+original model. From the distribution of the open dots, this appears quite
+problematic in this figure (many open dots are outside the predicted range; many
+predicted interactions are not existing), and this questions the usefulness of
+the whole approach. Other traits may be needed; perhaps performing several
+regressions for different broad taxonomic groups may also improve the approach,
+and widen its applicability.
 
-\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The fact that our
-model over-predict the number of interactions is abundantly discussed in the
-manuscript (along with why, and how to overcome it), so we will not elaborate
-further on it in this reply. In the original niche model paper, it is true
-that $c$ is not constrained by $n$. However, the purposes of the two models are
-not the same. The niche model allows to generate a distribution of network
-properties based only on connectance and richness. We add allometric
-informations so as to be able to estimate species-level interactions in addition
-to network properties. The allometric relationshipss on which we rely are well
-documented. As for the fact that other traits can be added, this is discussed in
-the manuscript at several places, including a whole figure. We made no changes
-to the manuscript.}}
+\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The $c$ is
+constrained by $n$ in the original niche model: it is drawn uniformly
+between $r/2$ and $n$, with the expected value of $r$ being $2Cn$.}}
+
+\textit{\textcolor{blue}{The fact that our model over-predict the number of
+interactions is discussed in the manuscript (along with why, and how to overcome
+it). However, the purposes of the two models are not the same. The niche model
+allows to generate a distribution of network properties based only on
+connectance and richness. We add allometric informations so as to be able to
+estimate species-level interactions in addition to network properties. The
+allometric relationshipss on which we rely are well documented. As for the fact
+that other traits can be added, this is discussed in the manuscript at several
+places, including a figure. }}
 

### 2013-06-18 ms_V3.tex
Biblio_fusion+lines numberingin the review +orthograph corrections

@@
 \usepackage[style=bes]{biblatex}
-\bibliography{./library, EKLOF,CHEUNG,THUILLER,CANARD, POISOT, WILLIAMS, HAVENS, BAISER, PEREIRA, WHITEHEAD, STOUFFER, STOU2, ALLESINA, ALLOUCHE, ALBOUY, FROESE, JACKSON,STANKO}
-%\bibliograph{library}
+\bibliography{./library}
 
@@
 infer the existence of interactions between two species require a good knowledge
-of their behaviour or a direct observation of interactions. In this paper, we
+of their behavior or a direct observation of interactions. In this paper, we
 overcome these limitations by developing a method, inspired from the niche model
@@
 predators and preys increases. We finally illustrate the potential of the method
-to infer the metaweb structure of pelagic fishes of the Meditarrannean sea under
+to infer the metaweb structure of pelagic fishes of the Mediterranean sea under
 different global change scenarios.
@@
 never co-occurred proves challenging, as traditional empirical methods of food
-web sampling such as stomacal content analysis cannot be applied. While for
+web sampling such as stomach content analysis cannot be applied. While for
 competitive communities this task could be achieved using predictive modeling
@@
 our understanding of large scale food web structure and our capacity to
-anticipate major changes in ecosystem functionning. Theory should provide some
+anticipate major changes in ecosystem functioning. Theory should provide some
 guidance about the general rules underpinning interactions among a set of
@@
 it is robust to sampling effort. We finally illustrate the potential of the
-method to infer the metaweb structure of pelagic fishes of the Meditarrannean
+method to infer the metaweb structure of pelagic fishes of the Mediterranean
 sea and the consequences of alteration of body size distribution by global
@@
 \item[Step 2:] Statistical analysis of the predator-prey body size relationship;
-\item[Step 3:] Inferrence of the niche model parameters for all species from the species pool;
+\item[Step 3:] Inference of the niche model parameters for all species from the species pool;
 \item[Step 4:] Interpretation of the parameters and computation of the metaweb.
 \end{description}
-We also provide an example of R code (R Core Development Team) and data in the Supplementary Material, detailling the step by step procedure and the format of the input data.
+We also provide an example of R code (R Core Development Team) and data in the Supplementary Material, detailing the step by step procedure and the format of the input data.
 
@@
 Fig. 2). We note them as $r_{low,i}$ and $r_{high,j}$ respectively, and the
-corresponding parameters of the linear quantile regresions are
+corresponding parameters of the linear quantile regressions are
 $\beta_{0,low/high}$ and $\beta_{1,low/high}$. In sum, the parameter $n_i$ for
@@
 not impact the prediction since it will not affect parameter evaluation. It will
-however reduce the fit of the predator-prey body size relationship and therfore
+however reduce the fit of the predator-prey body size relationship and therefore
 the accuracy of the method if the species do have different body sizes. The same
-artifact will be observed if there is strong intraspecific variation in body
+artifact will be observed if there is strong intra-specific variation in body
 size (see the Discussion).
@@
 
-\subsection{Inferring the metaweb for Mediterrannean fishes}
+\subsection{Inferring the metaweb for Mediterranean fishes}
 We estimated parameters $n$, $c$ and $r$ for each of the 557 species and
 inferred the potential interactions among all of them (the example in the
-Supplementariy code is based on this dataset). The metaweb has a total of 126
+Supplementary code is based on this dataset). The metaweb has a total of 126
 501 links, for a connectance of 0.41 (Fig. 5A). The metaweb is also highly
@@
 the minimum or maximum known for the species. Species' bathymetric ranges were
-obtained from FishBase \parencite{Froese2010, Louisy2005}. The resulting metaweb
+obtained from FishBase \parencite{Froese2011, Louisy2005}. The resulting metaweb
 has a total of 95 989 links, for a connectance of $C = 0.31$. Connectance
-decreases because links are removed by incomptabilities in bathymetry but the
+decreases because links are removed by incompatibilities in bathymetry but the
 total number of species stays constant. This metaweb is clearly less interval
@@
 distribution (the number of in and out feeding links per species), are
-controlled by the input parameters (species richness and connectance), wherea
+controlled by the input parameters (species richness and connectance), where
 all properties of our parameterized niche model are emergent features of the
@@
 predict gaps in the interaction matrix. The original niche model was definitely
-inspired by the predator-prey body size relationship, but was intented to be
+inspired by the predator-prey body size relationship, but was intended to be
 more general and eventually deal with several niche axes
@@
 
-Our application with the Mediterannean pelagic fish food web provides an example
+Our application with the Mediterranean pelagic fish food web provides an example
 of how straightforward it is to add additional information so as to improve the
-parameterization. A similar approach could also build on the comptability of
+parameterization. A similar approach could also build on the compatibility of
 other traits such as phenology, location in the water column or hunting modes.
@@
 stimulating discussion. DG received financial support from NSERC and Canada
-Research Chair program. TP is funded by a MELS-FQRNT post-doctoral fellowship.
+Research Chair program. TP and CA are funded by a MELS-FQRNT post-doctoral fellowship.
 \newpage
@@
 food web structure for the 11 food webs. A) Relationship between the TSS and the
-$R^2$ of the predator-prey body size relationship. B) Partitionning of the
+$R^2$ of the predator-prey body size relationship. B) Partitioning of the
 different components of the TSS.
@@
 \subsection*{Figure 5} 
-Illustration of the metaweb of the Mediterannean pelagic
+Illustration of the metaweb of the Mediterranean pelagic
 fishes (interactions in black). Panel A) represents the full metaweb and B) the
-same metaweb for which links between species not co-occuring together were
-removed (their range overlap for less than $0.1\%$ of the Mediterannean sea).
+same metaweb for which links between species not co-occurring together were
+removed (their range overlap for less than $0.1\%$ of the Mediterranean sea).
 
@@
 Impacts of altering the body size distribution of
-Meditarrennean fishes on the degree distribution of the metaweb. The black line
+Mediterranean fishes on the degree distribution of the metaweb. The black line
 corresponds to the original metaweb degree distribution. For the first scenario,

### 2013-06-18 replies.tex

@@
 \usepackage{color}
+\usepackage[style=bes]{biblatex}
+\bibliography{./library}
 
-\begin{document} \begin{onehalfspacing} \begin{center} \large{Response to
+\begin{document} \begin{onehalfspacing} \begin{center} \LARGE{Response to
 Reviewer: Inferring food web structure from predator-prey body size
@@
 
+\medskip
+
 Dominique Gravel, Timoth\'ee Poisot, Camille Albouy, Laure Velez, David Mouillot
-\begin{center} Reviewer 2: \end{center}
+
+\medskip
+\begin{center} \large{Reviewer 2: }\end{center}
 
@@
 This is why we made a mention of this opportunity toward the end of the discussion.
-But it's right we only mentionned it and did not developped our ideas any further.
-We added the following lines (LXXX) to the discussion:}}
+But it's right we only mentioned it and did not developed our ideas any further.
+We added the following lines (Lines 375-389) to the discussion:}}
 
-\textcolor{blue}{Bayesian inference appears a good candidate to achieve goal.
-It offers the possibility to constrain the prior distribution of the likelihood of any pairwise interaction, based on trait matching, using alternative source of data.
-The method we employed here was based on the match between predator and prey traits.
-This method could be generalized by looking at the match between all potential traits.
-Eklof et al.
-(2013) indeed found that the match between only three traits is enough to encompass a vast majority of interactions.
-But when such data is not always available, then it might be possible to use phylogeny as a proxy for a high dimensional trait species, provided that traits are conserved along the phylogeny (Mouquet et al.
-2012).
-A bayesian addition to the model would be to weight the likelihood that species $j$ is a predator of species $i$, considering that the closest relative of this predator is also a predator of $i$.
-It could account for part of the unexplained variation we found in our analysis, for instance by constraining the range of the diet for some large predators or by creating holes within the feeding range (Rall et al.
-2011).}
+\medskip \textcolor{blue}{Bayesian inference appears a good candidate to achieve goal. It
+offers the possibility to constrain the prior distribution of the likelihood of
+any pairwise interaction, based on trait matching, using alternative source of
+data. The method we employed here was based on the match between predator and
+prey traits. This method could be generalized by looking at the match between
+all potential traits. \textcite{Eklof2013} indeed found that the match between
+only three traits is enough to encompass a vast majority of interactions. But
+when such data is not always available, then it might be possible to use
+phylogeny as a proxy for a high dimensional trait species, provided that traits
+are conserved along the phylogeny \parencite{Mouquet2012}. A bayesian addition
+to the model would be to weight the likelihood that species $j$ is a predator of
+species $i$, considering that the closest relative of this predator is also a
+predator of $i$. It could account for part of the unexplained variation we found
+in our analysis, for instance by constraining the range of the diet for some
+large predators or by creating holes within the feeding range
+\parencite{Rall2011}}
 
@@
 on the x-axis of the figure. We have analyzed these relationship for a variety
-of food webs (Digel et al. 2011), but I could imagine that the methods
+of food webs \parencite{Digel2011}, but I could imagine that the methods
 introduced here would allow a more thorough investigation of this relationship.
@@
 \medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{This is certainly an intriguing result coming out from our analysis.
-We also find this result interesting because it links to some of our previous work on persistence in metacommunities and our current work on the biogeography of body size.
-We also had a discussion with Neo Martinez at a previous workshop about this relationship, he was curious to see if his assumption of a linear relationship between the niche and the range of the diet was confirmed (Williams and Martinez, 2000).
+We also find this result interesting because it links to some of our previous work on persistence in meta-communities and our current work on the biogeography of body size.
+We also had a discussion with Neo Martinez at a previous workshop about this relationship, he was curious to see if his assumption of a linear relationship between the niche and the range of the diet was confirmed  \parencite{Williams2000}.
 There are already a large number of figures in the paper (6) so we prefer not to add a new one, that could already be guessed from the Fig.
 2.
-We however added the following discussion (at PXLX):}}
+We however added the following discussion (at Page 14-15; Lines 331-346):}}
 
-\textcolor{blue}{It appears at Fig.
+\medskip\textcolor{blue}{It appears at Fig.
 2 that the feeding range increases with the body size of the predator.
@@
 This relationship will have to be investigated further, among several food webs (e.g.
-Digel et al.
-2011), because the scaling of generality with trophic rank has several consequences on persistence (Gravel et al.
-2011) and food web dynamics (e.g.
-Brose et al.
-2006, Berlow et al.
-2009).}
+\textcite{Digel2011}), because the scaling of generality with trophic rank has several consequences on persistence \parencite{Gravel2011b} and food web dynamics \parencite{Brose2006,Berlow2009}.}
 
@@
 potential links that are realized from local to landscape scales was the central
-topic of one of our prior projects (Brose et al. 2004). You might find this
+topic of one of our prior projects Brose et al. 2004. You might find this
 useful to support your assumption that meta-communities should include links
@@
 We are currently working on a theory for metawebs, trying to develop a framework to improve inference of local web structure given the probability of the interactions in the metaweb.
-This approach considers the likelihood of an interaction between a pair of species given their co-occurrence andfavorable environmental conditions.
+This approach considers the likelihood of an interaction between a pair of species given their co-occurrence and favorable environmental conditions.
 This topic is however beyond the topic of the current paper.
@@
 \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We corrected
-accordingly by replacing the abbrevation B by M}}
+accordingly by replacing the abbreviation B by M}}
 
@@
 
-\begin{center} Reviewer 3: \end{center}
+\newpage
+\begin{center} {\large Reviewer 3:} \end{center}
 
@@
 
+\medskip 
 \medskip \textbf{\large{Main comments:}}
@@
 working at the local or regional scale. In the text, we give examples at both
-these scales (locally in figures 2 and 3, regionaly in figure 5). We do agree
+these scales (locally in figures 2 and 3, regionally in figure 5). We do agree
 with the fact that additional information will make the predictions better; this
@@
 co-occurence along the depth gradient) is pictured in Fig. 5b. This is also
-explicitly written in the discussion (L. XXX-XXX). We corrected the abstract and the last paragraph of the introduction to make clear that our metholody applies at both the local and metaweb scales.}}
+explicitly written in the discussion (Lines  319-322).
+We corrected the abstract and the last paragraph of the introduction to make clear that our methodology applies at both the local and metaweb scales.}}
 
@@
 
-\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The study of Rohr et al.
-(2010), does not allow to evaluate the parameters of a new species entering a local community, neither the metaweb (which is the object of the current study).
+\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The study of  \textcite{Rohr2010}, does not allow to evaluate the parameters of a new species entering a local community, neither the metaweb (which is the object of the current study).
 It is therefore not possible to infer the potential links an immigrating species will do with the resident species.
@@
 Based on these arguments, we believe that the method  will be used for instance to study the interactions in emerging communities following global changes.}}
+\medskip
 
@@
 ii) we are not aware of any quantile regression that could account for uncertainty in the independent variable.
-We added a mention to this issue at LXXX.}}
+We added a mention to this issue at Lines 167-168.}}
+\medskip 
+%---------------%
 
-%---------------% 
 \medskip l.50: The use of "emergent" sounds strange here.
@@
 
-\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{ We replaced the word "emergent" by "novel".}}
+\medskip\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{ We replaced the word "emergent" by "novel".}}
 
@@
 
-\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We modified the sentence to avoid amiguities.
+\medskip\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We modified the sentence to avoid ambiguities.
 The metaweb gives interactions among a given set of species, wether at local or regional scales.}}
@@
 
-\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{See the above responses to previous comments.}}
+\medskip\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{See the above responses to previous comments.}}
 
@@
 
-\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{This is a basic
+\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{This is a basic
 postulate of the niche model. We have added a reference to the original paper to
@@
 
-\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The
+\medskip\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The
   \emph{dotted} lines. We corrected accordingly and apologize for the mistake.}}
@@
 
-\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{These are the parameters of the linear quantile regressions. The sentence was corrected accordingly.}}
+\medskip\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{These are the parameters of the linear quantile regressions. The sentence was corrected accordingly.}}
 
@@
 
-\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{No. The centroid
+\medskip\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{No. The centroid
 is a function of the two body sizes (hence $\alpha$), while the range limits are
 a function of the predator body size and its range.}}
+`
+\medskip
 
@@
 
-\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{Whether the
+\medskip\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{Whether the
 correct prediction of absence or presence of an interaction is the most
 interesting part of a model is ultimately a matter of personal taste, and
-adequation to the study objectives. Given that (especialy when no other traits
+adequation to the study objectives. Given that (especially when no other traits
 than body size are included), this method tends to over-estimate the number of
@@
 important feature.}}
+\medskip
 
@@
 
-\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We corrected
+\medskip\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We corrected
 accordingly.}}
@@
 
-\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We argue it is an
+\medskip\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We argue it is an
 important piece of information, which was required by a previous reviewer. We
@@
 
-\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The choice of quantiles are left free to the user in the R code providing with this article, by default, we chose the most commonly used threshold of 5\% and 95\%.
+\medskip\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The choice of quantiles are left free to the user in the R code providing with this article, by default, we chose the most commonly used threshold of 5\% and 95\%.
 A threshold of 100\% would include all interactions, but would tend to overpredict the link density.}}
@@
 
-\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We corrected accordingly and apologize for the mistake}}
+\medskip\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We corrected accordingly and apologize for the mistake}}
 
@@
 
-\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The $c$ is
+\medskip\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The $c$ is
 constrained by $n$ in the original niche model: it is drawn uniformly
@@
 
-\textit{\textcolor{blue}{The fact that our model over-predict the number of
+\medskip\textit{\textcolor{blue}{The fact that our model over-predict the number of
 interactions is discussed in the manuscript (along with why, and how to overcome
@@
 estimate species-level interactions in addition to network properties. The
-allometric relationshipss on which we rely are well documented. As for the fact
+allometric relationships on which we rely are well documented. As for the fact
 that other traits can be added, this is discussed in the manuscript at several
 places, including a figure. }}
+
+\newpage
+ \printbibliography
 
